\section{New Implications}
\label{sec:new-impls}

\begin{lemma}
\label{thm:impl:mxs-to-ef1-n2}
Let $([2], [m], (v_1, v_2), w)$ be a fair division instance with indivisible items.
If $v_1$ is additive and agent 1 is MXS-satisfied by allocation $A$,
then agent 1 is also EF1-satisfied by $A$.
\end{lemma}
\begin{proof}
Suppose $A$ is MXS-fair to agent 1 but not EF1-fair to her.
Then agent 1 envies agent 2 in $A$, so $v_1(A_1) < v_1(A_2)$.
Let $B$ be agent 1's MXS-certificate for $A$. Then $v_1(B_1) \le v_1(A_1)$.
Moreover, $v_1(A_2) = v_1([m]) - v_1(A_1) \le v_1([m]) - v_1(B_1) = v_1(B_2)$.
Hence, we get $v_1(B_1) \le v_1(A_1) < v_1(A_2) \le v_1(B_2)$.

Let $G \defeq \{g \in [m]: v_1(g) > 0\}$ and $C \defeq \{c \in [m]: v_1(c) < 0\}$.
Let $\max(\emptyset) \defeq -\infty$ and $\min(\emptyset) \defeq \infty$.

Since agent 1 is EFX-satisfied by $B$ and not EF1-satisfied by $A$,
for every $\ghat \in A_2$, we get
\begin{align*}
& \frac{v_1(A_2) - v_1(\ghat)}{w_2} > \frac{v_1(A_1)}{w_1}
\ge \frac{v_1(B_1)}{w_1}
\\ &\ge \frac{1}{w_2}\left(v_1(B_2) - \min_{g \in B_2 \cap G} v_1(g)\right)
\\ &\ge \frac{1}{w_2}\left(v_1(A_2) - \min_{g \in B_2 \cap G} v_1(g)\right).
\end{align*}
Hence, for every $\ghat \in A_2$, we get $v_1(\ghat) < \min_{g \in B_2 \cap G} v_1(g)$.
Hence, $A_2 \cap G$ and $B_2 \cap G$ are disjoint, so $A_2 \cap G \subseteq B_1 \cap G$.
Also, for every $\chat \in A_1$, we get
\begin{align*}
& \frac{d_1(A_1) - d_1(\chat)}{w_1} > \frac{d_1(A_2)}{w_2}
\ge \frac{d_2(B_2)}{w_2}
\\ &\ge \frac{1}{w_1}\left(d_1(B_1) - \min_{c \in B_1 \cap C} d_1(c)\right)
\\ &\ge \frac{1}{w_1}\left(d_1(A_1) - \min_{c \in B_1 \cap C} d_1(c)\right).
\end{align*}
Hence, for every $\chat \in A_1$, we have $d_1(\chat) < \min_{c \in B_1 \cap C} d_1(c)$.
Hence, $A_1 \cap C$ and $B_1 \cap C$ are disjoint, so $B_1 \cap C \subseteq A_2 \cap C$.
Hence,
\begin{align*}
v_1(A_2) &= v_1(A_2 \cap G) - d_1(A_2 \cap C)
\\ &\le v_1(B_1 \cap G) - d_1(B_1 \cap C) = v_1(B_1),
\end{align*}
which is a contradiction.
Hence, it's not possible for $A$ to be MXS-fair to agent 1 but not EF1-fair to her.
\end{proof}

\begin{lemma}
\label{thm:impl:eef1-to-prop1}
For a fair division instance $([n], [m], (v_i)_{i=1}^n, w)$,
if an allocation $X$ is epistemic-EF1-fair to agent $i$, then $X$ is also PROP1-fair to $i$
if one of these conditions hold:
\begin{tightenum}
\item $v_i$ is subadditive and the items are chores to agent $i$.
\item $v_i$ is additive and $w_i \le w_j$ for all $j \in [n] \setminus \{i\}$.
\item $v_i$ is additive and $n=2$.
\end{tightenum}
\end{lemma}
\begin{proof}
Suppose agent $i$ is epistemic-EF1-satisfied but not PROP1-satisfied by allocation $X$.
Let $A$ be agent $i$'s epistemic-EF1-certificate for $X$.
Then $A$ is EF1-fair to agent $i$.
If $A$ is PROP1-fair to $i$, then $X$ would also be PROP1-fair to agent $i$,
which is a contradiction. Hence, $A$ is not PROP1-fair to $i$.
Therefore, all of these hold:
\begin{tightenum}
\item $v_i(A_i) < w_iv_i([m])$.
\item $v_i(A_i \cup \{g\}) \le w_iv_i([m])$ for all $g \in [m] \setminus A_i$.
\item $v_i(A_i \setminus \{c\}) \le w_iv_i([m])$ for all $c \in A_i$.
\end{tightenum}

Since $v_i$ is subadditive, there exists $j \in [n] \setminus \{i\}$ such that $v_i(A_j) > w_jv_i([m])$
(otherwise $v_i([m]) \le \sum_{j=1}^n v_i(A_j) < \sum_{j=1}^n w_jv_j([m]) = v_i([m])$). Hence,
\[ \frac{v_i(A_i)}{w_i} < v_i([m]) < \frac{v_i(A_j)}{w_j}. \]
Hence, $i$ envies $j$. But $i$ is EF1-satisfied. Hence,
\\ $\exists c \in A_i$ such that
    $\displaystyle \frac{v_i(A_i \setminus \{c\})}{w_i} \ge \frac{v_i(A_j)}{w_j}$,
\\ or $\exists g \in A_j$ such that
    $\displaystyle \frac{v_i(A_i)}{w_i} \ge \frac{v_i(A_j \setminus \{g\})}{w_j}$.

\textbf{Case 1}: $\exists c \in A_i$ such that $v_i(A_i \setminus \{c\})/w_i \ge v_i(A_j)/w_j$.

Since $i$ is PROP1-unsatisfied and $v_i(A_j) > w_jv_i([m])$, we get
\[ \frac{v_i(A_j)}{w_j} \le \frac{v_i(A_i \setminus \{c\})}{w_i} \le v_i([m]) < \frac{v_i(A_j)}{w_j}, \]
which is a contradiction.
Hence, it's impossible for agent $i$ to be EF1-satisfied but not PROP1-satisfied by $A$ for this case.

\textbf{Case 2}: $\exists g \in A_j$ such that $v_i(A_i)/w_i \ge v_i(A_j \setminus \{g\})/w_j$.

First, we show that this case doesn't occur if all items in $A_j$ are chores.
Since $i$ envies $j$ but not EF1-envies $j$, we get
\begin{equation}
\label{eq:impl:eef1-to-prop1:gpos}
\frac{v_i(g \mid A_j \setminus \{g\})}{w_j}
= \frac{v_i(A_j) - v_i(A_j \setminus \{g\})}{w_j}
\ge \frac{v_i(A_j)}{w_j} - \frac{v_i(A_i)}{w_i} > 0.
\end{equation}
Hence, this case doesn't occur if all items in $A_j$ are chores.

Since $i$ is not PROP1-satisfied, we get
\begin{align*}
& \frac{v_i(A_i) + v_i(g \mid A_i)}{w_i} \le w_i([m]) < \frac{v_i(A_j)}{w_j}
\\ &\implies \frac{v_i(g \mid A_i)}{w_i} < \frac{v_i(A_j)}{w_j} - \frac{v_i(A_i)}{w_i}
    \le \frac{v_i(g \mid A_j \setminus \{g\})}{w_j}.
\end{align*}

Let $v_i$ be additive. Then we get
\[ \frac{v_i(g)}{w_i} < \frac{v_i(g)}{w_j} \implies w_j < w_i. \]
If $w_i \le w_j$ for all $j \in [n] \setminus \{i\}$, we get a contradiction.

Now suppose $v_i$ is additive and $n=2$.
Then the agents are $i$ and $j$. Note that $w_i + w_j = 1$.
Let $\ghat \in \argmax_{t \in A_j} v_i(t)$.
Since $i$ is not PROP1-satisfied, we get
\begin{align*}
& v_i(A_i \cup \{\ghat\}) \le w_iv_i([m]) = w_iv_i(A_i \cup \{\ghat\}) + w_iv_i(A_j \setminus \{\ghat\})
\\ &\implies \frac{v_i(A_i \cup \{\ghat\})}{w_i} \le \frac{v_i(A_j \setminus \{\ghat\})}{w_j}.
\end{align*}
Based on the assumption of Case 2, we get
\[ \frac{v_i(A_i)}{w_i} \ge \frac{v_i(A_j \setminus \{g\})}{w_j} \ge \frac{v_i(A_j \setminus \{\ghat\})}{w_j}. \]
Hence,
\[ v_i(A_i \cup \{\ghat\}) \le \frac{w_i}{w_j}v_i(A_j \setminus \{\ghat\}) \le v_i(A_i). \]
Therefore, $v_i(\ghat) \le 0$.
Since $\ghat$ is the most-valuable item in $A_j$ to $i$, we get that $v_i(g) \le 0$,
which contradicts \eqref{eq:impl:eef1-to-prop1:gpos}.
Hence, it's impossible for agent $i$ to be EF1-satisfied but not PROP1-satisfied by $A$ for this case.
\end{proof}

\begin{lemma}
\label{thm:mms-to-mxs}
Let $\Ical \defeq ([n], [m], (v_i)_{i=1}^n, w)$ be a fair division instance with equal entitlements.
Let allocation $A$ be MMS-fair to agent $i$.
Then $A$ is also MXS-fair to $i$ if at least one of these conditions hold:
\begin{tightenum}
\item All items are goods to agent $i$.
\item $v_i$ is additive.
\end{tightenum}
\end{lemma}
\begin{proof}
We will show that agent $i$'s leximin $n$-partition is her MXS-certificate for $A$,
which would prove that $A$ is MXS-fair to agent $i$.

Without loss of generality, assume $i = 1$.
Let $P$ be a leximin $n$-partition of $v_1$ (c.f.~\cref{defn:leximin})
such that $v_1(P_1) \le v_1(P_2) \le \ldots \le v_1(P_n)$.
Then $v_1(P_1) = \MMS_{v_1}^n([m]) \le v_1(A_1)$.

For any agent $j \ge 2$, the allocation $(P_1, P_j)$ is leximin for
the instance $\Icalhat \defeq (\{i, j\}, P_1 \cup P_j, (v_1, v_j), (1/2, 1/2))$.
Hence, agent 1 is MMS-satisfied by $(P_1, P_j)$ in $\Icalhat$.
Since either all items are goods to agent 1 or $v_1$ is additive,
by \cref{thm:impl:mms-to-efx-n2}, agent 1 is EFX-satisfied by $(P_1, P_j)$ in $\Icalhat$.

On considering all values of $j$, we get that agent 1 is EFX-satisfied by $P$ in $\Ical$.
Hence, $P$ is agent 1's MXS-certificate for $A$.
\end{proof}

\begin{lemma}
\label{thm:impl:eefx-to-propx}
Consider a fair division instance $([n], [m], (v_i)_{i=1}^n, w)$ where
the items are chores to agent $i$ and $v_i$ is subadditive.
If an allocation $A$ is epistemic-EFX-fair to agent $i$,
then it is also PROPx-fair to agent $i$.
\end{lemma}
\begin{proof}
Suppose $A$ is epistemic-EFX-fair to agent $i$ but not PROPx-fair to $i$.
Let $B$ be agent $i$'s epistemic-EFX-certificate for $A$.
Then $B$ is also PROPx-unfair to $i$.

Since $i$ is EFX-satisfied with $B$, we get that for all $j \in [n] \setminus \{i\}$,
\[ \min_{S \in \Scal} \frac{v_i(B_i \setminus S)}{w_i} \ge \frac{v_i(B_j)}{w_j}, \]
where $\Scal \defeq \{S \subseteq B_i: v_i(S \mid B_i \setminus S) < 0\}$.
Add these inequalities for all $j$, weighting each by $w_j$, to get
\[ \min_{S \in \Scal} \frac{v_i(B_i \setminus \{c\})}{w_i} > \sum_{j=1}^n v_i(B_j) \ge v_i([m]), \]
which implies that $B$ is PROPx-fair, a contradiction.
Hence, there can't be an allocation $A$ that is epistemic-EFX-fair to $i$
but not PROPx-fair to $i$.
\end{proof}

\begin{lemma}
\label{thm:impl:efx-to-propm}
Let $([n], [m], (v_i)_{i=1}^n, w)$ be a fair division instance
where $v_i$ is additive for some agent $i$.
If an allocation $A$ is EFX-fair to agent $i$, then it is also PROPm-fair to agent $i$
if at least one of these conditions holds:
\begin{tightenum}
\item $w_i \le w_j$ for all $j \in [n] \setminus \{i\}$, and $v_i(A_i) \ge 0$.
\item $n=2$.
\end{tightenum}
\end{lemma}
\begin{proof}
Suppose agent $i$ is EFX-satisfied but not PROPm-satisfied by allocation $A$.
Then for some agent $\jhat \in [n] \setminus \{i\}$, we have
\[ \frac{v_i(A_i)}{w_i} < v_i([m]) < \frac{v_i(A_{\jhat})}{w_{\jhat}}. \]

Since $i$ doesn't EFX-envy $\jhat$, for all $S \subseteq A_i$ such that
$v_i(S \mid A_i \setminus S) < 0$, we get
\[ \frac{v_i(A_i \setminus S)}{w_i} \ge \frac{v_i(A_{\jhat})}{w_{\jhat}} > v_i([m]). \]
Hence, condition \ref{item:propm:chores} (chores condition) of PROPm is satisfied.
Since condition \ref{item:propm:goods} (goods condition) of PROPm is not satisfied, we get that
$T \neq \emptyset$ and $v_i(A_i) + \max(T) \le w_iv_i([m])$.
%
For all $j \in T$, we get
\begin{align}
\frac{v_i(A_i)}{w_i} &\ge \frac{\max(\{v_i(A_j \setminus S): S \subseteq A_j \textrm{ and } v_i(S \mid A_i) > 0\})}{w_j}
    \tag{$i$ doesn't EFX-envy $j$}
\\ &= \frac{v_i(A_j)}{w_j} - \frac{\min(\{v_i(S): S \subseteq A_j \textrm{ and } v_i(S) > 0\})}{w_j}
    \notag
\\ &= \frac{v_i(A_j)}{w_j} - \frac{\tau_j}{w_j} \ge \frac{v_i(A_j)}{w_j} - \frac{\max(T)}{w_j}.
    \label{eqn:impl:efx-to-propm:1}
\end{align}

\textbf{Special case 1}: $w_i \le w_j$ for all $j \in [n] \setminus \{i\}$, and $v_i(A_i) \ge 0$.

Let $J \defeq \{j \in [n] \setminus \{i\}: \tau_j > 0\}$.
For all $j \in J$, using \eqref{eqn:impl:efx-to-propm:1}, we get
\[ \frac{v_i(A_i) + \max(T)}{w_i}
\ge \frac{v_i(A_j)}{w_j} - \frac{\max(T)}{w_j} + \frac{\max(T)}{w_i}
\ge \frac{v_i(A_j)}{w_j}. \]

For all $j \in [n] \setminus (J \cup \{i\})$, we have $\tau_j = 0$, so $v_i(A_j) \le 0$. Hence,
\[ \frac{v_i(A_i)}{w_i} \ge 0 \ge \frac{v_i(A_j)}{w_j}. \]
Therefore,
\[ v([m]) = \sum_{j=1}^n w_j\left(\frac{v_i(A_j)}{w_j}\right)
    < \sum_{j=1}^n w_j\left(\frac{v_i(A_i) + \max(T)}{w_i}\right)
    = \frac{v_i(A_i) + \max(T)}{w_i}. \]
Hence, condition 1 of PROPm is satisfied, which is a contradiction.
Hence, it's impossible for $i$ to be EFX-satisfied by $A$ but not PROPm-satisfied by $A$.

\textbf{Special case 2}: $n=2$

Let the two agents be $i$ and $j$. Since $T \neq \emptyset$, we have $\max(T) = \tau_j > 0$.
Since $i$ is not PROPm-satisfied by $A$, we get
\begin{align}
& v_i(A_i) + \tau_j \le w_iv_i([m]) = w_iv_i(A_i) + w_iv_i(A_j)
\\ &\implies w_jv_i(A_i) + \tau_j \le w_iv_i(A_j)
\\ &\implies \frac{v_i(A_i)}{w_i} \le \frac{v_i(A_j)}{w_j} - \frac{\tau_j}{w_iw_j}
    \le \frac{v_i(A_j)}{w_j} - \frac{\tau_j}{w_j}.
\end{align}
Combining this with equation \eqref{eqn:impl:efx-to-propm:1} gives us $\tau_j = 0$, which is a contradiction.
Hence, it's impossible for $i$ to be EFX-satisfied by $A$ but not PROPm-satisfied by $A$.
\end{proof}

\begin{lemma}
\label{thm:impl:mms-to-aps-n2}
Let $([2], [m], (v_i)_{i=1}^n, w)$ be a fair division instance.
If $v_k$ is additive for some agent $k$, then $\APS_k \le \WMMS_k$.
If entitlements are equal, then $\APS_k = \MMS_k$.
\end{lemma}
\begin{proof}
Let
\[ \beta_k \defeq \max(\{v_k(S)/w_i: S \subseteq [m], i \in [2], v_k(S) \le w_iv_k([m])\}). \]
Then $\WMMS_k = w_k\beta_k$, since there are only two agents and $v_k$ is additive.
Let $p^*$ be the optimal APS price vector. Let
\[ S^* \defeq \argmax_{S \subseteq [m]: p^*(S) \le w_kp^*([m])} v_k(S). \]
Then $\APS_k = v_k(S^*)$. Since $\APS_k \le w_kv_k([m])$, we get
$\APS_k/w_k \le \beta_k = \WMMS_k/w_k$. Hence, $\APS_k \le \WMMS_k$.

When entitlements are equal, $\APS_k \ge \pessShare_k = \MMS_k$ by \cref{thm:impl:aps-to-pess}.
\end{proof}
