\section{Fairness Notions}
\label{sec:notions}

We now describe all the different fairness notions we consider in this paper.

\subsection{Envy-Based Notions}

We begin with the most well-known notion of fairness: envy-freeness (EF).

\begin{definition}[EF]
\label{defn:ef}
Let $\Ical \defeq (N, M, (v_i)_{i \in N}, w)$ be a fair division instance.
In an allocation $A$, an agent $i \in N$ \emph{envies} another agent $j \in N \setminus \{i\}$ if
$\frac{v_i(A_i)}{w_i} < \frac{v_i(A_j)}{w_j}$.
Agent $i$ is \emph{envy-free} in $A$ (or $A$ is EF-fair to $i$) if
she doesn't envy any other agent in $A$.
\end{definition}

When entitlements are unequal, most papers use the term WEF instead of EF.
But we use the term EF in this paper to emphasize that unequal entitlements
is a property of the fair division setting, not the fairness notion.

It is easy to see that EF allocations may not exist, so several relaxtions have been studied.
Two of the most popular relaxations of EF are EF1 and EFX.
EF1 was proposed by \cite{budish2011combinatorial,lipton2004approximately},
and EFX was proposed by \cite{caragiannis2019unreasonable}.

\begin{definition}
\label{defn:ef1}
For a fair division instance $\Ical \defeq (N, M, (v_i)_{i \in N}, w)$,
an allocation $A$ is EF1-fair to agent $i$ if for every other agent $j$,
at least one of the following hold:
\begin{tightenum}
\item $i$ does not envy $j$.
\item $\exists g \in A_j$ such that
    $\displaystyle \frac{v_i(A_i)}{w_i} \ge \frac{v_i(A_j \setminus \{g\})}{w_j}$.
\item $\exists c \in A_i$ such that
    $\displaystyle \frac{v_i(A_i \setminus \{c\})}{w_i} \ge \frac{v_i(A_j)}{w_j}$.
\end{tightenum}
\end{definition}

\begin{definition}
\label{defn:efx}
For a fair division instance $\Ical \defeq (N, M, (v_i)_{i \in N}, w)$,
an allocation $A$ is EFX-fair to agent $i$ if for every other agent $j$,
$i$ doesn't envy $j$, or both of the following hold:
\begin{enumerate}
\item $\displaystyle \frac{v_i(A_i)}{w_i} \ge \frac{\max(\{v_i(A_j \setminus S) \mid S \subseteq A_j
    \textrm{ and } v_i(S \mid A_i) > 0 \textrm{ and } v_i(S \mid A_j \setminus S) \ge 0\})}{w_j}$.
\item $\displaystyle \frac{\min(\{v_i(A_i \setminus S) \mid S \subseteq A_i
    \textrm{ and } v_i(S \mid A_i \setminus S) < 0 \})}{w_i} \ge \frac{v_i(A_j)}{w_j}$.
\end{enumerate}
\end{definition}

\Cref{defn:efx} looks very different from the original definition of EFX
given by \cite{caragiannis2019unreasonable}.
However, in \cref{sec:notions:efx}, we explain why \cref{defn:efx} makes sense,
and we show that it's equivalent to the original definition when
valuations are submodular and the items are goods.

\subsection{Proportionality-Based Notions}

\begin{definition}[PROP]
\label{defn:prop}
For a fair division instance $\Ical \defeq (N, M, (v_i)_{i \in N}, w)$,
agent $i$'s \emph{proportional share} is $w_iv_i(M)$.
Allocation $A$ is \emph{proportional} (PROP) if $v_i(A_i) \ge w_iv_i(M)$.
\end{definition}

\begin{definition}[PROP1 \cite{conitzer2017fair}]
\label{defn:prop1}
For a fair division instance $\Ical \defeq (N, M, (v_i)_{i \in N}, w)$,
an allocation $A$ is PROP1-fair to agent $i$ if at least one of the following hold:
\begin{tightenum}
\item $v_i(A_i) \ge w_iv_i(M)$.
\item $v_i(A_i \cup \{g\}) > w_iv_i(M)$ for some $g \in M \setminus A_i$.
\item $v_i(A_i \setminus \{c\}) > w_iv_i(M)$ for some $c \in A_i$.
\end{tightenum}
\end{definition}

Note that \cref{defn:prop1} uses strict inequalities, whereas most papers don't.
However, we define it this way to make it a slightly stronger fairness notion.
Also, this nuance doesn't affect most results, except those involving
binary (or negative binary) valuations.

\begin{definition}[PROPx \cite{aziz2020polynomial,li2022almost}]
\label{defn:propx}
For a fair division instance $\Ical \defeq (N, M, (v_i)_{i \in N}, w)$,
an allocation $A$ is said to be PROPx-fair to agent $i$ iff
either $v_i(A_i) \ge w_iv_i(M)$ or both of these conditions hold:
\begin{tightenum}
\item $v_i(A_i \cup S) > w_iv_i(M)$ for every $S \subseteq M \setminus A_i$
    such that $v_i(S \mid A_i) > 0$.
\item $v_i(A_i \setminus S) > w_iv_i(M)$ for every $S \subseteq A_i$
    such that $v_i(S \mid A_i \setminus S) < 0$.
\end{tightenum}
\end{definition}

\Cref{defn:propx} looks different from other well-known definitions of PROPx
\cite{aziz2020polynomial,li2022almost}.
However, this is because those definitions were for more restricted settings,
and for those settings, we show that our definition is equivalent to theirs
(\cref{sec:notions:propx}).

\begin{definition}[PROPm]
\label{defn:propm}
Let $(N, M, (v_i)_{i \in N}, w)$ be a fair division instance.
An allocation $A$ is said to be PROPm-fair to agent $i$ iff
$v_i(A_i) \ge w_iv_i(M)$ or both of these conditions hold:
\begin{tightenum}
\item\label{item:propm:chores}$v_i(A_i \setminus S) > w_iv_i(M)$ for every $S \subseteq A_i$
    such that $v_i(S \mid A_i \setminus S) < 0$.
\item\label{item:propm:goods}For every $j \in N \setminus \{i\}$, define
    \[ \tau_j \defeq \begin{cases}
    0 & \textrm{ if } v_i(S \mid A_i) \le 0 \textrm{ for all } S \subseteq A_j
    \\ \min(\{v_i(S \mid A_i) \mid S \subseteq A_j \textrm{ and } v_i(S \mid A_i) > 0\}) & \textrm{ otherwise}
    \end{cases}. \]
    Define $T \defeq \{\tau_j \mid j \in N \setminus \{i\} \textrm{ and } \tau_j > 0\}$.
    Then either $T = \emptyset$, or $v_i(A_i) + \max(T) > w_iv_i(M)$.
\end{tightenum}
\end{definition}

PROPm was originally defined in \cite{baklanov2021achieving} for additive goods.
However, that definition has a minor error, which we explain in \cref{sec:notions:propm}.
\Cref{defn:propm} fixes the error.

\subsection{Maximin Share and AnyPrice Share}

Share-based notions are those where each agent $i$ has a threshold $\mu_i$,
and an allocation $A$ is fair to agent $i$ if $v_i(A_i) \ge \mu_i$.
We get different fairness notions depending on how we define $\mu_i$,
e.g., we get proportionality with $\mu_i \defeq v_i(M)/|N|$.
(A more precise definition of share-based notions is given in \cite{babaioff2022fair}).
Here we describe two share-based notions, maximin share (MMS) and AnyPrice share (APS).

\begin{definition}[MMS \cite{budish2011combinatorial}]
\label{defn:mms}
For a finite set $M$, let $\Pi_n(M)$ be the set of all $n$-partitions of $M$.
For a function $f: 2^M \to \mathbb{R}$, define
\[ \MMS_f^n(M) \defeq \max_{P \in \Pi_n(M)} \min_{j=1}^n f(P_j). \]
%
Let $\Ical \defeq (N, M, (v_i)_{i \in N}, w)$ be a fair division instance
with equal entitlements (i.e., $w_i = 1/|N|$ for all $i \in N$).
Agent $i$'s \emph{maximin share} (MMS) is given by $\MMS_{v_i}^{|N|}(M)$.
When the instance $\Ical$ is clear from context, we write $\MMS_i$ instead of $\MMS_{v_i}^{|N|}(M)$.
An allocation $A$ is MMS-fair to agent $i$ if $v_i(A_i) \ge \MMS_{v_i}^{|N|}(M)$.
A partition $P \in \Pi_n(M)$ for which $\min_{j=1}^n v_i(P_j) = \MMS_i$
is called agent $i$'s \emph{MMS partition}.
\end{definition}

For unequal entitlements, there are two extensions of MMS:
weighted MMS (WMMS) and pessimistic share (pessShare).

\begin{definition}[WMMS \cite{farhadi2019fair}]
\label{defn:wmms}
Let $\Ical \defeq (N, M, (v_i)_{i \in N}, w)$ be a fair division instance.
Let $\Acal$ be the set of all allocations for $\Ical$.
Then agent $i$'s \emph{weighted maximin share} (WMMS) is
\[ \WMMS_i := w_i \max_{X \in \Acal} \min_{j \in N} \frac{v_i(X_j)}{w_j}. \]
An allocation $A$ is WMMS-fair to agent $i$ if $v_i(A_i) \ge \WMMS_i$.
An allocation $X$ that maximizes $w_i \min_{j \in N} \frac{v_i(X_j)}{w_j}$
is called agent $i$'s \emph{WMMS partition}.
\end{definition}

\begin{definition}[pessShare \cite{babaioff2023fair}]
\label{defn:pessShare}
Let $1 \le \ell \le d$. Let $\Pi_d(M)$ be the set of all $d$-partitions of $M$.
Then agent $i$'s $\ell$-out-of-$d$ share is defined as
\[ \loodM_i := \max_{\substack{X \in \Pi_d(M):\\v_i(X_j) \le v_i(X_{j+1}) \forall j \in [d-1]}} \sum_{j=1}^{\ell} v_i(X_j). \]
Then agent $i$'s pessimistic share is defined as
\[ \pessShare_i := \sup_{1 \le \ell \le d:\;\ell / d \le w_i} \loodM_i. \]
Allocation $A$ is pessShare-fair to agent $i$ if $v_i(A_i) \ge \pessShare_i$.
\end{definition}

For equal entitlements, it's trivial to show that $\WMMS_i = \MMS_i$.
In \cref{thm:pess-is-mms} (\cref{sec:notions:mms}),
we show that $\pessShare_i = \MMS_i$ for equal entitlements.

Unless stated otherwise, in settings with potentially unequal entitlements,
by MMS we mean weighted MMS.

The notion AnyPrice Share (APS) \cite{babaioff2023fair} has two equivalent definitions: primal and dual.

For any non-negative integer $m$, define
$\Delta_m \defeq \{x \in \mathbb{R}^m_{\ge 0}: \sum_{j=1}^m x_j = 1\}$.
For any $x \in \mathbb{R}^m$ and $S \subseteq [m]$, define $x(S) \defeq \sum_{j=1}^m x_j$.

\begin{definition}[APS (primal)]
\label{defn:aps}
For a fair division instance $\Ical \defeq ([n], [m], (v_i)_{i=1}^n, w)$,
agent $i$'s AnyPrice Share (APS) is defined as
\[ \APS_i \defeq \min_{p \in \mathbb{R}^m}\;\max_{S \subseteq [m]: p(S) \le w_ip([m])} v_i(S). \]
Here $p$ is called the \emph{price vector}.
A vector $p^* \in \mathbb{R}^m$ is called an \emph{optimal} price vector if
\[ p^* \in \argmin_{p \in \mathbb{R}^m}\;\max_{S \subseteq [m]: p(S) \le w_ip([m])} v_i(S). \]
\end{definition}

\Cref{defn:aps} is slightly different from the original definition given in \cite{babaioff2023fair}.
However, they assume that either all items are goods or all items are chores,
and for those special cases, their definition is equivalent to \cref{defn:aps}.
This follows from \cref{thm:aps-optimal-price} (c.f.~\cref{sec:notions:aps}).

\begin{definition}[APS (dual)]
\label{defn:aps-dual}
Let $\Ical \defeq ([n], [m], (v_i)_{i=1}^n, w)$ be a fair division instance.
For an agent $i$ and any $z \in \mathbb{R}$, let $\Scal_z \defeq \{S \subseteq [m]: v_i(S) \ge z\}$.
Then agent $i$'s AnyPrice share, denoted by $\APS_i$, is the largest value $z$ such that
\[ \exists x \in \mathbb{R}_{\ge 0}^{\Scal_z}, \sum_{S \in \Scal_z} x_S = 1
    \textrm{ and } \left(\forall j \in [m], \sum_{S \in \Scal_z: j \in S} x_S = w_i\right). \]
\end{definition}

\Cref{defn:aps-dual} can be interpreted as a linear programmming relaxation of MMS.
Formally, when entitlements are equal, adding the integrality constraints
$nx_S \in \mathbb{Z}_{\ge 0}$ for all $S \in \Scal_z$ gives us an alternate definition of MMS.

\cite{babaioff2023fair} show that the primal and dual definitions of APS are equivalent.
They prove this only for goods, but their proof can be easily adapted to the case of mixed manna.
For completeness sake, we prove this in \cref{thm:aps-primal-dual-equiv} (\cref{sec:notions:aps}).

Closely related to maximin share is the notion of \emph{leximin partition}.

\begin{definition}
\label{defn:leximin}
For any set $S \subseteq M$, let $\Pi_n(S)$ denote the set of all $n$-partitions of $S$.
For any sequence $X = (x_i)_{i=1}^n$ of real numbers, define $\sorted(X)$ to be a permutation of $X$
where entries occur in non-decreasing order.
For any two sequences $X = (x_i)_{i=1}^n$ and $Y = (y_i)_{i=1}^n$, we say that $X \le Y$ if
$\exists i \in [n]$ such that $x_i \le y_i$ and $x_j = y_j$ for all $j \in [i-1]$.
(Note that this relation $\le$ over sequences is a total ordering.)

We say that $P \in \Pi_n([m])$ is a leximin $n$-partition of a function $f: 2^{[m]} \to \mathbb{R}$ if
\[ P \in \argmax_{X \in \Pi_n([m])} \sorted\left((f(X_j))_{j=1}^n\right). \]
\end{definition}

It is easy to see that if $P$ is a leximin $n$-partition of $f: 2^{[m]} \to \mathbb{R}$,
then $\min_{j=1}^n f(P_j) = \MMS_f^n([m])$.

\subsection{Derived Notions}

New fairness notions can be obtained by systematically modifying existing notions.

We start with two related concepts, epitemic fairness \cite{aziz2018knowledge,caragiannis2023new}
and minimum fair share \cite{caragiannis2023new}.

\begin{definition}[epistemic fairness]
\label{defn:epistemic}
Let $F$ be a fairness notion.
An allocation $A$ is \emph{epistemic-$F$-fair} to an agent $i$ if
there exists another allocation $B$ that is $F$-fair to agent $i$ and $B_i = A_i$.
$B$ is called agent $i$'s \emph{epistemic-$F$-certificate} for $A$.
\end{definition}

\begin{definition}[minimum fair share]
\label{defn:minfs}
For a fair division instance $\Ical \defeq (N, M, (v_i)_{i \in N}, w)$
and fairness notion $F$, let $\Acal(\Ical, F, i)$ be the set of allocations
that are $F$-fair to agent $i$.
Then $i$'s \emph{minimum $F$ share} is given by
\[ \minFS(\Ical, F, i) \defeq \min_{A \in \Acal(\Ical, F, i)} v_i(A_i). \]
An allocation $A$ is \emph{minimum-$F$-share-fair} to agent $i$ if
$v_i(A_i) \ge \minFS(\Ical, F, i)$.

Equivalently, $A$ is minimum-$F$-share-fair to agent $i$ if there exists
an allocation $B \in \Acal(\Ical, F, i)$ such that $v_i(A_i) \ge v_i(B_i)$.
Then $B$ is called agent $i$'s \emph{minimum-$F$-share-certificate} for $A$.
\end{definition}

We now describe pairwise fairness \cite{caragiannis2019unreasonable}
and groupwise fairness \cite{barman2018groupwise}.

\begin{definition}[restricting]
\label{defn:restricting}
Let $\Ical \defeq (N, M, (v_i)_{i \in N}, w)$ be a fair division instance
and $A$ be an allocation. For a subset $S \subseteq N$ of agents, where $|S| \ge 2$,
let $\restrict(\Ical, A, S)$ be the pair $(\Icalhat, \Ahat)$, where
$\Ahat \defeq (A_j)_{j \in S}$, $\Icalhat \defeq (S, \Mhat, (v_j)_{j \in S}, \what)$,
$\Mhat \defeq \bigcup_{j \in S} A_j$, and $\what_j \defeq w_j / \sum_{j \in S} w_j$.
\end{definition}

\begin{definition}[pairwise fairness]
\label{defn:pairwise}
For a fair diviion instance $\Ical \defeq (N, M, (v_i)_{i \in N}, w)$,
an allocation $A$ is called \emph{pairwise-$F$-fair} to agent $i$ if
for all $j \in N \setminus \{i\}$, $A^{(j)}$ is $F$-fair to $i$ in the instance $\Ical^{(j)}$,
where $(\Ical^{(j)}, A^{(j)}) \defeq \restrict(\Ical, A, \{i, j\})$.
\end{definition}

\begin{definition}[groupwise fairness]
\label{defn:groupwise}
For a fair diviion instance $\Ical \defeq (N, M, (v_i)_{i \in N}, w)$,
an allocation $A$ is called \emph{groupwise-$F$-fair} to agent $i$ if
for all $S \subseteq N \setminus \{i\}$, $A^{(S)}$ is $F$-fair to $i$ in the instance $\Ical^{(S)}$,
where $(\Ical^{(S)}, A^{(S)}) \defeq \restrict(\Ical, A, \{i\} \cup S)$.
\end{definition}

In this paper, we consider the following derivative notions:
\begin{tightenum}
\item Epistemic envy-freeness (EEF).
\item Epistemic EFX (EEFX).
\item Epistemic EF1 (EEF1).
\item Minimum EF share (MEFS).
\item Minimum EFX share (MXS).
\item Minimum EF1 share (M1S).
\item Pairwise proportionality (PPROP) and groupwise proportionality (GPROP).
\item Pairwise MMS (PMMS) and groupwise MMS (GMMS).
\item Pairwise APS (PAPS) and groupwise APS (GAPS).
\end{tightenum}
