\section{Proofs of Implications}
\label{sec:impls-extra}

\subsection{Among Derived Notions}
\label{sec:impls-extra:among-derived}

\begin{remark}
\label{thm:impl:epistemic}
For any fairness notion $F$, if an allocation is $F$-fair to an agent $i$,
then it is also epistemic-$F$-fair to agent $i$.
If an allocation is epistemic-$F$-fair to an agent $i$,
then it is also minimum-$F$-share-fair to agent $i$.
If there are only two agents, then an allocation is epistemic-$F$-fair to an agent $i$
iff it is $F$-fair to agent $i$.
\end{remark}

\begin{remark}
\label{thm:impl:groupwise}
For any fairness notion $F$, if an allocation is groupwise-$F$-fair to an agent $i$,
then it is also pairwise-$F$-fair to agent $i$ and $F$-fair to agent $i$.
When there are only two agents, all three of these notions are equivalent.
\end{remark}

\begin{lemma}
\label{thm:impl:ext-to-epistemic}
Let $\Omega$ be a set containing pairs of the form $(\Ical, A)$,
where $\Ical$ is a fair division instance and $A$ is an allocation for $\Ical$.
For any two fairness notions $F_1$ and $F_2$, let $\phi(F_1, F_2)$ be the proposition
``\,$\forall (\Ical, A) \in \Omega$, for every agent $i$ in $\Ical$,
$A$ is $F_2$-fair to $i$ whenever $A$ is $F_1$-fair to $i$". Then
$\phi(F_1, F_2) \implies \phi(\textrm{epistemic-}F_1, \textrm{epistemic-}F_2)
\textrm{ and } \phi(\textrm{min-}F_1\textrm{-share}, \textrm{min-}F_2\textrm{-share})$.
\end{lemma}
\begin{proof}
Suppose $\phi(F_1, F_2)$.
Pick any $(\Ical, A) \in \Omega$.
Let $\Ical \defeq ([n], [m], (v_i)_{i=1}^n, w)$.
Pick any $i \in [n]$.

Suppose $A$ is epistemic-$F_1$-fair to $i$.
Let $B$ be $i$'s epistemic-$F_1$-certificate for $A$.
Then $B$ is $F_1$-fair to $i$ and $A_i = B_i$.
By $\phi(F_1, F_2)$, $B$ is also $F_2$-fair to $i$.
Hence, $B$ is $i$'s epistemic-$F_2$-certificate for $A$.
Therefore, $\phi(\textrm{epistemic-}F_1, \textrm{epistemic-}F_2)$ holds.

Suppose $A$ is min-$F_1$-share-fair to $i$.
Let $B$ be $i$'s min-$F_1$-share-certificate for $A$.
Then $B$ is $F_1$-fair to $i$ and $v_i(A_i) \ge v_i(B_i)$.
By $\phi(F_1, F_2)$, $B$ is also $F_2$-fair to $i$.
Hence, $B$ is $i$'s min-$F_2$-share-certificate for $A$.
Therefore, $\phi(\textrm{min-}F_1\textrm{-share}, \textrm{min-}F_2\textrm{-share})$ holds.
\end{proof}

\subsection{Among EF, EFX, EF1}
\label{sec:impls-extra:among-ef-efx-ef1}

Here we look at implications among EF, EFX, EF1, and their epistemic variants.

\begin{remark}[EF $\fimplies$ EFX+EF1]
\label{thm:impl:ef-to-efx+ef1}
If an allocation is EF-fair to agent $i$, then it is also EFX-fair to $i$ and EF1-fair to $i$.
\end{remark}

Because of how we define EFX (\cref{defn:efx}),
it's not always true that EFX implies EF1.
However, it's true for many common settings, as the following lemma shows.

\begin{lemma}[EFX $\fimplies$ EF1]
\label{thm:impl:efx-to-ef1}
For the fair division instance $([n], [m], (v_i)_{i=1}^n, w)$,
let $A$ be an allocation where agent $i$ is EFX-satisfied.
Then agent $i$ is EF1-satisfied in these scenarios:
\begin{tightenum}
\item $v_i$ is additive.
\item $v_i$ is doubly strictly monotone, i.e., $[m] = G \cup C$, $v_i(g \mid \cdot) > 0$
    for every $g \in G$, and $v_i(c \mid \cdot) < 0$ for every $c \in C$.
\item Agents have equal entitlements, $v_i$ is submodular, and all items are goods for agent $i$.
\item $v_i$ is submodular and all items are chores for agent $i$.
\end{tightenum}
\end{lemma}
\begin{proof}
Suppose $i$ is EFX-satisfied but not EF1-satisfied.
Suppose $i$ EF1-envies $j$.

Since $i$ EF1-envies $j$, we get that for all $t \in A_j$, we have
\[ \frac{v_i(A_i)}{w_i} < \frac{v_i(A_j \setminus \{t\})}{w_j}. \]
Since $i$ is EFX-satisfied, we get that
for all $t \in A_j$ such that $v_i(t \mid A_i) > 0$, we have
\[ \frac{v_i(A_i)}{w_i} \ge \frac{v_i(A_j \setminus \{t\})}{w_j}. \]
Hence, for all $t \in A_j$, we get $v_i(t \mid A_i) \le 0$.

Since $i$ EF1-envies $j$, we get that for all $t \in A_i$, we have
\[ \frac{v_i(A_i \setminus \{t\})}{w_i} < \frac{v_i(A_j)}{w_j}. \]
Since $i$ is EFX-satisfied, we get that
for all $t \in A_i$ such that $v_i(t \mid A_i \setminus \{t\}) < 0$, we have
\[ \frac{v_i(A_i \setminus \{t\})}{w_i} \ge \frac{v_i(A_j)}{w_j}. \]
Hence, for all $t \in A_i$, we get $v_i(t \mid A_i \setminus \{t\}) \ge 0$.

If $v_i$ is additive, we get $v_i(A_i) \ge 0 \ge v_i(A_j)$, which is a contradiction.
%
If $v_i$ is doubly strictly monotone, then
all items in $A_j$ are chores and all items in $A_i$ are goods.
Hence, $v_i(A_i) \ge 0 \ge v_i(A_j)$, which is a contradiction.

Suppose all agents have equal entitlements, all items are goods for $i$, and $v_i$ is submodular.
Let $A_j \defeq \{g_1, \ldots, g_k\}$. Then
\[ v_i(A_j \mid A_i) = \sum_{t=1}^k v_i(g_t \mid A_i \cup \{g_1, \ldots, g_{t-1}\})
\le \sum_{t=1}^k v_i(g_t \mid A_i) \le 0. \]
Hence, $v_i(A_j) \le v_i(A_i \cup A_j) = v_i(A_i) + v_i(A_j \mid A_i) \le v_i(A_i)$.
This is a contradiction.

Suppose all items are chores for $i$ and $v_i$ is submodular.
Let $A_i = \{c_1, \ldots, c_k\}$. Then
\[ v_i(A_i) = \sum_{t=1}^k v_i(c_t \mid \{c_1, \ldots, c_{t-1}\})
\ge \sum_{t=1}^k v_i(c_t \mid A_i \setminus \{c_t\}) \ge 0. \]
Hence, $v_i(A_i) \ge 0 \ge v_i(A_j)$, which is a contradiction.

A contradiction implies that it's impossible for agent $i$ to be
EFX-satisfied but not EF1-satisfied.
\end{proof}

\begin{lemma}[MXS $\fimplies$ EF1 for $n=2$]
\label{thm:impl:mxs-to-ef1-n2}
Let $([2], [m], (v_1, v_2), w)$ be a fair division instance with indivisible items.
If $v_1$ is additive and agent 1 is MXS-satisfied by allocation $A$,
then agent 1 is also EF1-satisfied by $A$.
\end{lemma}
\begin{proof}
Suppose $A$ is MXS-fair to agent 1 but not EF1-fair to her.
Then agent 1 envies agent 2 in $A$, so $v_1(A_1) < v_1(A_2)$.
Let $B$ be agent 1's MXS-certificate for $A$. Then $v_1(B_1) \le v_1(A_1)$.
Moreover, $v_1(A_2) = v_1([m]) - v_1(A_1) \le v_1([m]) - v_1(B_1) = v_1(B_2)$.
Hence, we get $v_1(B_1) \le v_1(A_1) < v_1(A_2) \le v_1(B_2)$.

Let $G \defeq \{g \in [m]: v_1(g) > 0\}$ and $C \defeq \{c \in [m]: v_1(c) < 0\}$.
Let $\max(\emptyset) \defeq -\infty$ and $\min(\emptyset) \defeq \infty$.

Since agent 1 is EFX-satisfied by $B$ and not EF1-satisfied by $A$,
for every $\ghat \in A_2$, we get
\begin{align*}
& \frac{v_1(A_2) - v_1(\ghat)}{w_2} > \frac{v_1(A_1)}{w_1}
\ge \frac{v_1(B_1)}{w_1}
\\ &\ge \frac{1}{w_2}\left(v_1(B_2) - \min_{g \in B_2 \cap G} v_1(g)\right)
\\ &\ge \frac{1}{w_2}\left(v_1(A_2) - \min_{g \in B_2 \cap G} v_1(g)\right).
\end{align*}
Hence, for every $\ghat \in A_2$, we get $v_1(\ghat) < \min_{g \in B_2 \cap G} v_1(g)$.
Hence, $A_2 \cap G$ and $B_2 \cap G$ are disjoint, so $A_2 \cap G \subseteq B_1 \cap G$.
Let $d_i \defeq -v_i$ for all $i$. Then for every $\chat \in A_1$, we get
\begin{align*}
& \frac{d_1(A_1) - d_1(\chat)}{w_1} > \frac{d_1(A_2)}{w_2}
\ge \frac{d_2(B_2)}{w_2}
\\ &\ge \frac{1}{w_1}\left(d_1(B_1) - \min_{c \in B_1 \cap C} d_1(c)\right)
\\ &\ge \frac{1}{w_1}\left(d_1(A_1) - \min_{c \in B_1 \cap C} d_1(c)\right).
\end{align*}
Hence, for every $\chat \in A_1$, we have $d_1(\chat) < \min_{c \in B_1 \cap C} d_1(c)$.
Hence, $A_1 \cap C$ and $B_1 \cap C$ are disjoint, so $B_1 \cap C \subseteq A_2 \cap C$.
Hence,
\begin{align*}
v_1(A_2) &= v_1(A_2 \cap G) - d_1(A_2 \cap C)
\\ &\le v_1(B_1 \cap G) - d_1(B_1 \cap C) = v_1(B_1),
\end{align*}
which is a contradiction.
Hence, it's not possible for $A$ to be MXS-fair to agent 1 but not EF1-fair to her.
\end{proof}

We will now show that every MXS allocation is also M1S
when marginal values are \emph{doubly monotone}.
We first define double monotonicity (\cref{defn:dbl-mono}).
Then we state a simple observation on how EFX and EF1 are related.
Finally, we use that as the basis for an iterative algorithm
for computing an agent's M1S certificate using their MXS certificate.

\begin{definition}[doubly monotone]
\label{defn:dbl-mono}
For two sets $G$ and $C$, a function $v: 2^{[m]} \to \mathbb{R}$ is called
$(G, C)$-\emph{doubly-monotone} if $G \cap C = \emptyset$,
$G \cup C = [m]$, and $\forall\,R \subseteq [m]$,
we have $v(g \mid R) \ge 0$ for all $g \in G \setminus R$
and $v(c \mid R) \le 0$ for all $c \in C \setminus R$.
\end{definition}

\begin{observation}
\label{thm:special-efx-is-ef1}
Let $([n], [m], (v_i)_{i=1}^n, w)$ be a fair division instance
where $v_i$ is $(G, C)$-doubly-monotone.
If all of the following hold for an alloation $A$, then $A$ is EF1-fair to agent $i$.
\begin{tightenum}
\item $A$ is EFX-fair to agent $i$.
\item $v_i(g \mid A_i) > 0$ for all $g \in G \setminus A_i$.
\item $v_i(c \mid A_i \setminus \{c\}) < 0$ for all $c \in A_i \cap C$.
\end{tightenum}
\end{observation}

\begin{algorithm}[htb]
\caption{$\improve_i(Z)$: Here $Z$ is an allocation for the fair division instance
$([n], G \cup C, (v_j)_{j=1}^n, w)$.}
\label{algo:mxs-to-m1s}
\begin{algorithmic}[1]
\While{\texttt{true}}
    \If{$\exists g \in G \cap Z_j$ for some $j \in [n] \setminus \{i\}$ such that $v_i(g \mid Z_i) = 0$}
        \State $Z_i = Z_i \cup \{g\}$.
        \State $Z_j = Z_j \setminus \{g\}$.
    \ElsIf{$\exists c \in Z_i \cap C$ such that $v_i(c \mid Z_i \setminus \{c\}) = 0$}
        \State $Z_i = Z_i \setminus \{c\}$.
        \State Pick any $j \in [n] \setminus \{i\}$ and set $Z_j = Z_j \cup \{c\}$.
    \Else\label{alg-line:mxs-to-m1s:else}
        \State \label{alg-line:mxs-to-m1s:return}\Return $Z$.
    \EndIf
\EndWhile
\end{algorithmic}
\end{algorithm}

\begin{lemma}
\label{thm:impl:mxs-to-m1s}
Let $([n], [m], (v_i)_{i=1}^n, w)$ be a fair division instance
where $v_i$ is $(G, C)$-doubly-monotone.
If an allocation $A$ is MXS-fair to agent $i$,
then it is also M1S-fair to agent $i$ if $n=2$ or $G = \emptyset$.
\end{lemma}
\begin{proof}
\WLoG{}, let $i=1$. Let $B$ be agent 1's MXS-certificate for $A$.
Then $B$ is EFX-fair to agent 1 and $v_1(B_1) \le v_1(A_1)$.
Define $\Bhat \defeq \improve_1(B)$, where $\improve_1$ is defined in \cref{algo:mxs-to-m1s}.

In any iteration of the while loop in \cref{algo:mxs-to-m1s},
let $X$ be the allocation at the beginning of the iteration.
Either $X$ is returned at line \ref{alg-line:mxs-to-m1s:return},
or the allocation gets modified to $Y$, and (as we will prove soon) the following invariants hold:
\begin{tightenum}
\item If $X$ is EFX-fair to agent 1, then $Y$ is also EFX-fair to agent 1.
\item $|Y_1 \cap G| - |Y_1 \cap C| > |X_1 \cap G| - |X_1 \cap C|$.
\item $v_1(Y_1) = v_1(X_1)$.
\end{tightenum}
The first invariant ensures that $\Bhat$ is also EFX-fair to agent 1.
The second invariant ensures that $\improve_1$ terminates.
Then using \cref{thm:special-efx-is-ef1}, we get that $\Bhat$ is EF1-fair to agent 1.
The third invariant ensures that $v_1(\Bhat_1) = v_1(B_1) \le v_1(A_1)$,
which makes $\Bhat$ an M1S-certificate for allocation $A$ and agent 1.
The second and third invariants are trivial to show.
We now prove that the first invariant if $n = 2$ or $G = \emptyset$.

Suppose $Y_1 = X_1 \cup \{g\}$ and $Y_j = X_j \setminus \{g\}$,
where $g \in G \cap X_j$ such that $v_1(g \mid X_1) = 0$.
Since $G \neq \emptyset$, we have $n = 2$ and $j = 2$.
Pick any $S \subseteq Y_2$ such that $v_1(S \mid Y_1) > 0$. Then
\begin{align*}
v_1(S \cup \{g\} \mid X_1) &= v_1(S \cup \{g\} \cup X_1) - v_1(X_1)
\\ &= (v_1(S \cup Y_1) - v_1(Y_1)) + (v_1(Y_1) - v_1(X_1))
\\ &= v_1(S \mid Y_1) > 0.
\end{align*}
Since $X$ is EFX-fair to agent 1, we get
\[ \frac{v_1(Y_1)}{w_1} = \frac{v_1(X_1)}{w_1}
    \ge \frac{v_1(X_2 \setminus (S \cup \{g\}))}{w_2}
    = \frac{v_1(Y_2 \setminus S)}{w_j}, \]
so 1 doesn't EFX-envy agent $j$. Hence, 1 is EFX-satisfied by $Y$.

Suppose $Y_1 = X_1 \setminus \{c\}$ and $Y_j = X_j \cup \{c\}$,
where $c \in X_1 \cap C$ such that $v_1(c \mid X_1 \setminus \{c\}) = 0$.
Pick any $S \subseteq Y_1$ such that $v_1(S \mid Y_1 \setminus S) < 0$. Then
\begin{align*}
v_1(S \cup \{c\} \mid X_1 \setminus (S \cup \{c\}))
    &= v(X_1) - v_1(X_1 \setminus (S \cup \{c\}))
\\ &= (v(X_1) - v_1(Y_1)) + (v_1(Y_1) - v_1(Y_1 \setminus S))
\\ &= v_1(S \mid Y_1 \setminus S) < 0.
\end{align*}
Since $X$ is EFX-fair to agent 1, we get that
for any other agent $k \in [n] \setminus \{1\}$,
\[ \frac{v_1(Y_1 \setminus S)}{w_1} = \frac{v_1(X_1 \setminus (S \cup \{c\}))}{w_1}
    \ge \frac{v_1(X_k)}{w_k} \ge \frac{v_1(Y_k)}{w_k}. \]
Hence, agent 1 is EFX-satisfied with $Y$.

Hence, invariant 1 holds, so $\Bhat$ is agent 1's M1S-certificate for allocation $A$.
\end{proof}

\subsection{Among PROP-Based Notions}
\label{sec:impls-extra:among-prop-based}

\begin{lemma}[PROPx $\fimplies$ PROPavg]
\label{thm:impl:propx-to-propavg}
In a fair division instance $([n], [m], (v_i)_{i=1}^n, w)$,
if an allocation is PROPx-fair to agent $i$, then it is also PROPavg-fair to agent $i$.
\end{lemma}
\begin{proof}
Assume (for the sake of contradiction) that there is an allocation $A$ where
agent $i$ is PROPx-satisfied but not PROPavg-satisfied.
%
Since $i$ is not PROPavg-satisfied, we get $v_i(A_i) \le w_iv_i([m])$.
Since $i$ is PROPx-satisfied, we get

\begin{itemize}
\item $v_i(A_i \setminus S) > w_iv_i([m])$ for all $S \subseteq A_i$ such that
    $v_i(S \mid A_i \setminus S) < 0$.
\item $v_i(A_i \cup S) > w_iv_i([m])$ for all $S \subseteq [m] \setminus A_i$
    such that $v_i(S \mid A_i) > 0$.
\end{itemize}

Since $i$ is not PROPavg-satisfied, we get that $T \neq \emptyset$
and $v_i(A_i) + \Sum(T)/|T| \le w_iv_i([m])$ ($T$ is defined in \cref{defn:propavg}).
For each $\tau_j \in T$, we have $0 < \tau_j = v_i(S_j \mid A_i)$ for some $S_j \subseteq A_j$.
Since $A$ is PROPx-fair to $i$, we have $v_i(A_i) + \tau_j > w_iv_i([m])$ for all $\tau_j \in T$.
On averaging these inequalities, we get $v_i(A_i) + \Sum(T)/|T| > w_iv_i([m])$,
which implies that $A$ is PROPavg-satisfied, which is a contradiction.
Hence, if $i$ is PROPx-satisfied by $A$, then she is also PROPavg-satisfied by $A$.
\end{proof}

\begin{lemma}
\label{thm:submod-marginal-is-submod}
For any $X \subseteq \Omega$ and any submodular function $f: 2^{\Omega} \to \mathbb{R}$,
$f(\cdot \mid X)$ is submodular.
\end{lemma}
\begin{proof}
Let $P, Q \subseteq \Omega \setminus X$. Let $g(Y) \defeq f(Y \mid X)$. Then
\begin{align*}
& g(P) + g(Q)
\\ &= f(P \cup X) + f(Q \cup X) - 2f(X)
\\ &\ge f((P \cup X) \cup (Q \cup X)) + f((P \cup X) \cap (Q \cap X)) - 2f(X)
    \tag{by $f$'s submodularity}
\\ &= f((P \cup Q) \cup X) + f((P \cap Q) \cup X) - 2f(X)
    \tag{by De Morgan's law}
\\ &= g(P \cup Q) + g(P \cap Q).
\end{align*}
Hence, $g$ is submodular.
\end{proof}

\begin{lemma}[PROPm $\fimplies$ PROP1]
\label{thm:impl:propm-to-prop1}
For a fair division instance $([n], [m], (v_i)_{i=1}^n, w)$,
if an allocation $A$ is PROPm-fair to agent $i$, then it is also PROP1-fair to agent $i$
if at least one of these conditions holds:
\begin{tightenum}
\item $v_i$ is submodular.
\item $v_i$ is doubly strictly monotone, i.e., $[m] = G \cup C$, $v_i(g \mid \cdot) > 0$
    for every $g \in G$, and $v_i(c \mid \cdot) < 0$ for every $c \in C$.
\end{tightenum}
\end{lemma}
\begin{proof}
Suppose allocation $A$ is PROPm-fair to $i$ but not PROP1-fair to $i$. Then
\begin{tightenum}
\item\label{item:impl:propm-to-prop1:unprop}$v_i(A_i) < w_iv_i([m])$ (by PROP1 unfairness).
\item\label{item:impl:propm-to-prop1:unprop1-chores}$v_i(A_i \setminus \{c\}) \le w_iv_i([m])$
    for all $c \in A_i$ (by PROP1 unfairness).
\item\label{item:impl:propm-to-prop1:unprop1-goods}$v_i(A_i \cup \{g\}) \le w_iv_i([m])$
    for all $g \in [m] \setminus A_i$ (by PROP1 unfairness).
\item\label{item:impl:propm-to-prop1:propm-chores}$v_i(A_i \setminus \{c\}) > w_iv_i([m])$
    for all $c \in A_i$ such that $v_i(c \mid A_i \setminus \{c\}) < 0$ (by PROPm fairness).
\item\label{item:impl:propm-to-prop1:propm-goods}$T = \emptyset$ or $v_i(A_i) + \max(T) > w_iv_i([m])$
    (by PROPm fairness; c.f.~\cref{defn:propm} for the definition of $T$).
\end{tightenum}

By \ref{item:impl:propm-to-prop1:unprop1-chores} and \ref{item:impl:propm-to-prop1:propm-chores},
we get $v_i(c \mid A_i \setminus \{c\}) \ge 0$ for all $c \in A_i$.
We now show that $v_i(A_i) \ge 0$.
If $v_i$ is doubly strictly monotone, then $A_i$ only contains goods, so $v_i(A_i) \ge 0$.
Now suppose $v_i$ is submodular. Let $A_i = \{g_1, \ldots, g_k\}$. Then
\[ v_i(A_i) = \sum_{j=1}^k v_i(g_j \mid \{g_1, \ldots, g_{j-1}\})
    \ge v_i(g_j \mid A_i \setminus \{g_j\}) \ge 0. \]

Suppose $T = \emptyset$. Then $\tau_j = 0$ for all $j \in [n] \setminus \{i\}$.
Hence, for all $j \in [n] \setminus \{i\}$, we have $v_i(A_j \mid A_i) \le 0$.
If $v_i$ is doubly strictly monotone, then $[m] \setminus A_i$ contains only chores,
so $v_i([m] \setminus A_i \mid A_i) \le 0$. If $v_i$ is submodular, then
$v_i(\cdot \mid A_i)$ is subadditive by \cref{thm:submod-marginal-is-submod}, so
\[ v_i([m] \setminus A_i \mid A_i)
    \le \sum_{j \in [n] \setminus \{i\}} v_i(A_j \mid A_i) \le 0. \]
Hence, $v_i(A_i) \ge v_i([m])$.
If $v_i([m]) \le 0$, then $v_i(A_i) \ge 0 \ge w_iv_i([m])$,
and if $v_i([m]) \ge 0$, then $v_i(A_i) \ge v_i([m]) \ge w_iv_i([m])$.
This contradicts \ref{item:impl:propm-to-prop1:unprop}, so $T \neq \emptyset$.

Let $\max(T) = \tau_{\jhat} > 0$. By definition of $\tau_{\jhat}$, we get
\begin{align*}
0 < \tau_{\jhat} &= \min(\{v_i(S \mid A_i) \mid S \subseteq A_{\jhat} \textrm{ and } v_i(S \mid A_i) > 0\})
\\ &\le \min(\{v_i(g \mid A_i) \mid g \in A_{\jhat} \textrm{ and } v_i(g \mid A_i) > 0\}).
\end{align*}

\textbf{Case 1}: $v_i(g \mid A_i) \le 0$ for all $g \in A_{\jhat}$.
\\ If $v_i$ is doubly strictly monotone, then $A_{\jhat}$ only has chores,
and so $v_i(S \mid A_i) \le 0$ for all $S \subseteq A_{\jhat}$.
This contradicts the fact that $\tau_{\jhat} > 0$.
Now let $v_i$ be submodular.
Since $v_i(\cdot \mid A_i)$ is subadditive by \cref{thm:submod-marginal-is-submod},
for any $S \subseteq A_{\jhat}$, we get
$v_i(S \mid A_i) \le \sum_{c \in S} v_i(c \mid A_i) \le 0$.
This contradicts the fact that $\tau_{\jhat} > 0$.

\textbf{Case 2}: $v_i(\ghat \mid A_i) > 0$ for some $\ghat \in A_{\jhat}$.
\\ Then $\max(T) = \tau_{\jhat} \le v_i(\ghat \mid A_i)$.
By \ref{item:impl:propm-to-prop1:propm-goods}, we get
$w_iv_i([m]) < v_i(A_i) + \max(T) \le v_i(A_i \cup \{\ghat\})$.
But this contradicts \ref{item:impl:propm-to-prop1:unprop1-goods}.

Hence, it cannot happen that $i$ is PROPm-satisfied by $A$ but not PROP1-satisfied.
\end{proof}

\subsection{EF vs PROP}
\label{sec:impls-extra:ef-vs-prop}

Here we look at implications between EF (and its epistemic variants) and PROP.

\begin{lemma}[MEFS $\fimplies$ PROP, \cite{bouveret2016characterizing}]
\label{thm:impl:mefs-to-prop}
For a fair division instance $([n], [m], (v_i)_{i=1}^n, w)$,
if $v_i$ is subadditive and an allocation $A$ is MEFS-fair to $i$, then $A$ is also PROP-fair to $i$.
\end{lemma}
\begin{proof}
Let $B$ be agent $i$'s MEFS-certificate for $A$.
Then for all $j \in [n]$, we have $v_i(B_i)/w_i \ge v_i(B_j)/w_j$.
Sum these inequalities over all $j \in [n]$, weighting each by $w_j$,
to get $v_i(B_i)/w_i \ge \sum_{j=1}^n v_i(B_j)$.
Since $v_i$ is subadditive, we get $v_i([m]) \le \sum_{j=1}^n v_i(B_j)$.
Hence,
\[ \frac{v_i(A_i)}{w_i} \ge \frac{v_i(B_i)}{w_i} \ge \sum_{j=1}^n v_i(B_j) \ge v_i([m]). \]
\end{proof}

\begin{lemma}[EF $\fimplies$ GPROP]
\label{thm:impl:ef-to-gprop}
For a fair division instance $([n], [m], (v_i)_{i=1}^n, w)$,
if $v_i$ is subadditive and agent $i$ is envy-free in $A$,
then $A$ is groupwise-PROP-fair to $i$.
\end{lemma}
\begin{proof}
Let $S$ be a subset of agents containing $i$.
Let $\Ahat$ be the allocation obtained by restricting $A$ to $S$ (c.f.~\cref{defn:restricting}).
Then $i$ is also envy-free in $\Ahat$.
$i$ is also MEFS-satisfied by $\Ahat$, since $\Ahat$ is its own MEFS-certificate for agent $i$.
By \cref{thm:impl:mefs-to-prop}, agent $i$ is PROP-satisfied by $\Ahat$.
Since this is true for all $S$ containing $i$,
we get that $A$ is groupwise-PROP-fair to agent $i$.
\end{proof}

\begin{lemma}[PROP $\fimplies$ EF for idval]
\label{thm:impl:prop-to-ef-superadd-id}
In a fair division instance $([n], [m], (v_i)_{i=1}^n, w)$ with identical superadditive valuations,
a PROP allocation is also an EF allocation.
\end{lemma}
\begin{proof}
Let $v$ be the common valuation function. Let $A$ be a PROP allocation.
Then for each agent $i$, we have $v(A_i) \ge w_iv([m])$.
Suppose $v(A_k) > w_kv([m])$ for some agent $k$.
Sum these inequalities to get $\sum_{i=1}^n v(A_i) > v([m])$.
This contradicts superadditivity of $v$, so $v(A_i) = w_iv([m])$ for each agent $i$.
Hence, $v(A_i)/w_i = v([m])$ for all $i$, so $A$ is EF.
\end{proof}

\begin{lemma}[PROP $\fimplies$ EF for $n=2$]
\label{thm:impl:prop-to-ef-n2}
In the fair division instance $([2], [m], (v_1, v_2), w)$, for some agent $i$,
if $v_i$ is superadditive and agent $i$ is PROP-satisfied by allocation $A$,
then she is also envy-free in $A$.
\end{lemma}
\begin{proof}
Assume $i=1$ \wLoG. Then
\begin{align*}
& \frac{v_1(A_1)}{w_1} \ge v_1([m]) \ge v_1(A_1) + v_1(A_2)
\\ &\implies v_1(A_2) \le v_1(A_1)\left(\frac{1}{w_1} - 1\right) = w_2 \frac{v_1(A_1)}{w_1}.
\end{align*}
Hence, agent 1 does not envy agent 2.
\end{proof}

\begin{lemma}[PPROP $\fimplies$ GPROP]
\label{thm:impl:pprop-to-gprop}
For a fair division instance $([n], [m], (v_i)_{i=1}^n, w)$,
if $v_i$ is submodular and allocation $A$ is pairwise-PROP-fair to agent $i$
then $A$ is groupwise-PROP-fair to agent $i$.
\end{lemma}
\begin{proof}
Since $A$ is PPROP-fair to $i$, for all $j \in [n] \setminus \{i\}$, we get
\begin{align*}
& v_i(A_i) \ge \frac{w_i}{w_i + w_j}v_i(A_i \cup A_j)
\\ &\implies (w_i+w_j)v_i(A_i) \ge w_i(v_i(A_j \mid A_i) + v_i(A_i))
\\ &\implies w_j v_i(A_i) \ge w_i v_i(A_j \mid A_i).
\end{align*}
Sum these inequalities over all $j \in [n] \setminus \{i\}$ to get
\[ (1-w_i) v_i(A_i) \ge w_i \sum_{j \neq i} v_i(A_j \mid A_i). \]
By \cref{thm:submod-marginal-is-submod}, $v_i(\cdot \mid A_i)$ is subadditive. Hence,
\begin{align*}
& (1-w_i) v_i(A_i) \ge w_i \sum_{j \neq i} v_i(A_j \mid A_i)
    \ge w_i v_i([m] \setminus A_i \mid A_i)
\\ &\implies v_i(A_i) \ge w_i v_i([m]).
\end{align*}
Hence, agent $i$ is PROP-satisfied by $A$.
This also works if we restrict the allocation to a subset of agents,
so $i$ is also GPROP-satisfied by $A$.
\end{proof}

\subsection{EFX, EF1 vs PROPx, PROPm, PROP1}
\label{sec:impls-extra:efx-ef1-vs-propx-propm-prop1}

\begin{lemma}[MXS $\fimplies$ PROP1, Theorem 3 of \cite{caragiannis2023new}]
\label{thm:impl:mxs-to-prop1}
In a fair division instance with equal entitlements,
if $v_i$ is additive for some agent $i$, $v_i(g) \ge 0$ for every item $g$,
and an allocation $A$ is MXS-fair to agent $i$, then $A$ is also PROP1-fair to agent $i$.
\end{lemma}

\begin{lemma}[EEF1 $\fimplies$ PROP1 for chores]
\label{thm:impl:eef1-to-prop1-chores}
For a fair division instance $([n], [m], (v_i)_{i=1}^n, w)$
where all items are chores to agent $i$ and $v_i$ is subaditive,
if an allocation $X$ is epistemic-EF1-fair to agent $i$,
then $X$ is also PROP1-fair to $i$.
\end{lemma}
\begin{proof}
Suppose agent $i$ is EEF1-satisfied by $X$.
Let $A$ be agent $i$'s EEF1-certificate for $X$.
Suppose $A$ is not PROP1-fair to $i$, we get $v_i(A_i) < w_iv_i([m])$
and $v_i(A_i \setminus \{c\}) \le w_iv_i([m])$ for all $c \in A_i$.

Since $v_i$ is subadditive, there exists $j \in [n] \setminus \{i\}$
such that $v_i(A_j) > w_jv_i([m])$
(otherwise $v_i([m]) \le \sum_{j=1}^n v_i(A_j) < \sum_{j=1}^n w_jv_j([m]) = v_i([m])$). Hence,
\[ \frac{v_i(A_i)}{w_i} < v_i([m]) < \frac{v_i(A_j)}{w_j}. \]
Hence, $i$ envies $j$ in $A$. But $i$ is EF1-satisfied by $A$.
Hence, $\exists c \in A_i$ such that
\[ \frac{v_i(A_i \setminus \{c\})}{w_i} \ge \frac{v_i(A_j)}{w_j}. \]

Since $i$ is PROP1-unsatisfied and $v_i(A_j) > w_jv_i([m])$, we get
\[ \frac{v_i(A_j)}{w_j} \le \frac{v_i(A_i \setminus \{c\})}{w_i} \le v_i([m]) < \frac{v_i(A_j)}{w_j}, \]
which is a contradiction.
Hence, $A$ is PROP1-fair to $i$, and so, $X$ is PROP1-fair to agent $i$.
\end{proof}

\begin{lemma}[EEF1 $\fimplies$ PROP1]
\label{thm:impl:eef1-to-prop1-submod}
Consider a fair division instance $([n], [m], (v_i)_{i=1}^n, w)$
where $v_i$ is submodular for some agent $i$
and $w_i \le w_j$ for all $j \in [n] \setminus \{i\}$.
If an allocation $X$ is epistemic-EF1-fair to agent $i$,
then $X$ is also PROP1-fair to $i$.
\end{lemma}
\begin{proof}
Suppose agent $i$ is EEF1-satisfied by $X$.
Let $A$ be agent $i$'s EEF1-certificate for $X$.
Then $A$ is EF1-fair to $i$.
We will show that $A$ is PROP1-fair to $i$
(which would prove that $X$ is also PROP1-fair to $i$).
This is trivial if $A$ is PROP-fair to $i$,
so assume $A$ is not PROP-fair to $i$, i.e., $v_i(A_i) < w_iv_i([m])$.

By \cref{thm:submod-marginal-is-submod}, we get that
$v_i(\cdot \mid A_i)$ is subadditive. Hence,
\[ v_i([m]) = v_i(A_i) + v_i([m] \setminus A_i \mid A_i)
    \le v_i(A_i) + \sum_{j \neq i} v_i(A_j \mid A_i). \]
Hence, for some $j \in [n] \setminus \{i\}$,
we get $v_i(A_j \mid A_i) > w_jv_i([m])$. Hence,
\[ \frac{v_i(A_i)}{w_i} < v_i([m]) < \frac{v_i(A_j \mid A_i)}{w_j} \le \frac{v_i(A_j)}{w_j}. \]
Hence, $i$ envies $j$ in $A$. Since $A$ is EF1-fair to $i$, we get two cases:

\textbf{Case 1}: $\exists c \in A_i$ such that
    $\displaystyle \frac{v_i(A_i \setminus \{c\})}{w_i} \ge \frac{v_i(A_j)}{w_j}$.
\\ Then $v_i(A_i \setminus \{c\}) > w_iv_i([m])$, so $A$ is PROP1-fair.

\textbf{Case 2}: $\exists g \in A_j$ such that
    $\displaystyle \frac{v_i(A_i)}{w_i} \ge \frac{v_i(A_j \setminus \{g\})}{w_j}$.
\begin{align*}
& \frac{v_i(A_i \cup \{g\})}{w_i}
    = \frac{v_i(A_i)}{w_i} + \frac{v_i(g \mid A_i)}{w_i}
\\ &\ge \frac{v_i(A_j \setminus \{g\})}{w_j} + \frac{v_i(g \mid A_i)}{w_j}
    \tag{$w_i \le w_j$}
\\ &\ge \frac{v_i(A_j \setminus \{g\} \mid A_i) + v_i(g \mid A_i)}{w_j}
    \tag{$v_i$ is submodular}
\\ &\ge \frac{v_i(A_j \mid A_i)}{w_j}
    \tag{$v_i(\cdot \mid A_i)$ is subadditive}
\\ &> v_i([m]).
\end{align*}
Hence, $A$ is PROP1-fair to $i$.

In both cases, we get that $A$ is PROP1-fair to $i$.
Hence, $X$ is also PROP1-fair to $i$.
\end{proof}

\begin{lemma}[EF1 $\fimplies$ PROP1 for $n=2$]
\label{thm:impl:ef1-to-prop1-n2}
Consider a fair division instance $([2], [m], (v_1, v_2), w)$,
where $v_i$ is subadditive for some agent $i$.
If an allocation $A$ is EF1-fair to agent 1,
then it is also PROP1-fair to agent 1 if at least one of the following hold:
\begin{tightenum}
\item $v_1(g \mid A_2 \setminus \{g\}) \le 0$ for all $g \in A_2$.
\item $v_1(g \mid A_1) > 0$ for some $g \in A_2$.
\item $v_1$ is submodular.
\end{tightenum}
\end{lemma}
\begin{proof}
If $A$ is PROP-fair to agent 1, then we are done,
so assume $A$ is not PROP-fair to agent 1.
By subadditivity of $v_1$, we get
$v_1([m]) \le v_1(A_1) + v_1(A_2)$.
Since $v_1(A_1) < w_1v_1([m])$, we get $v_1(A_2) > w_2v_1([m])$.
Hence, $v_1(A_1)/w_1 < v_1([m]) < v_1(A_2)/w_2$, so agent 1 envies agent 2.
Since $A$ is EF1-fair to agent 1, there are two cases:

\textbf{Case 1}: $\exists c \in A_1$ such that
    $\displaystyle \frac{v_1(A_1 \setminus \{c\})}{w_1} \ge \frac{v_1(A_2)}{w_2}$.
\\ Then $v_1(A_1 \setminus \{c\}) > w_1v_1([m])$, so $A$ is PROP1-fair.

\textbf{Case 2}: $\exists \ghat \in A_2$ such that
    $\displaystyle \frac{v_1(A_1)}{w_1} \ge \frac{v_1(A_2 \setminus \{\ghat\})}{w_2}$.
\\ Since agent 1 envies agent 2, we get
\[ \frac{v_1(A_2)}{w_2} > \frac{v_1(A_2 \setminus \{\ghat\})}{w_2}
\implies v_1(\ghat \mid A_2 \setminus \{\ghat\}) > 0. \]
By subadditivity of $v_1$ and PROP-unfairness of $A$, we get
\begin{align*}
v_1([m]) &\le v_1(A_1 \cup \{\ghat\}) + v_1(A_2 \setminus \{\ghat\})
    \le v_1(A_1 \cup \{\ghat\}) + \frac{w_2}{w_1}v_1(A_1)
\\ &= \frac{v_1(A_1 \cup \{\ghat\})}{w_1} - \frac{w_2}{w_1}v_1(\ghat \mid A_1).
\end{align*}
Let $g^* \defeq \max_{g \in A_2} v_1(g \mid A_1)$. Then
\begin{align*}
v_1(A_1 \cup \{g^*\}) &= v_1(A_1 \cup \{\ghat\})
    + (v_1(g^* \mid A_1) - v_1(\ghat \mid A_1))
\\ &\ge w_1v_1([m]) + v_1(g^* \mid A_1) - (1-w_2)v_1(\ghat \mid A_1)
\\ &\ge w_1v_1([m]) + w_2v_1(g^* \mid A_1).
\end{align*}
If $v_1(g^* \mid A_i) > 0$, then $A$ is PROP1-fair to agent 1.

Suppose $v_1(g^* \mid A_i) \le 0$ and $v_1$ is submodular.
Then $v_1(g \mid A_1) \le 0$ for all $g \in A_2$.
By \cref{thm:submod-marginal-is-submod}, $v_1(\cdot \mid A_1)$ is subadditive.
Hence, $v_1(A_2 \mid A_1) \le \sum_{g \in A_2} v_1(g \mid A_1) \le 0$.
Hence, $v_1(M) = v_1(A_1) + v_1(A_2 \mid A_1) \le v_1(A_1)$,
which is a contradiction since $A$ is not PROP-fair to agent 1.
Hence, $v_1(g^* \mid A_i) > 0$ if $v_1$ is submodular,
and thus, $A$ is PROP1-fair to agent 1.
\end{proof}

\begin{lemma}[EEFX $\fimplies$ PROPx, Lemma 2.1 of \cite{li2022almost}]
\label{thm:impl:eefx-to-propx}
Consider a fair division instance $([n], [m], (v_i)_{i=1}^n, w)$ where
the items are chores to agent $i$ and $v_i$ is subadditive.
If an allocation $A$ is epistemic-EFX-fair to agent $i$,
then it is also PROPx-fair to agent $i$.
\end{lemma}
\begin{proof}
Suppose $A$ is epistemic-EFX-fair to agent $i$ but not PROPx-fair to $i$.
Let $B$ be agent $i$'s epistemic-EFX-certificate for $A$.
Then $B$ is also PROPx-unfair to $i$.

Since $i$ is EFX-satisfied with $B$, we get that for all $j \in [n] \setminus \{i\}$,
\[ \min_{S \in \Scal} \frac{v_i(B_i \setminus S)}{w_i} \ge \frac{v_i(B_j)}{w_j}, \]
where $\Scal \defeq \{S \subseteq B_i: v_i(S \mid B_i \setminus S) < 0\}$.
Add these inequalities for all $j$, weighting each by $w_j$, to get
\[ \min_{S \in \Scal} \frac{v_i(B_i \setminus \{c\})}{w_i} > \sum_{j=1}^n v_i(B_j) \ge v_i([m]), \]
which implies that $B$ is PROPx-fair, a contradiction.
Hence, there can't be an allocation $A$ that is epistemic-EFX-fair to $i$
but not PROPx-fair to $i$.
\end{proof}

\begin{lemma}[EFX $\fimplies$ PROPavg]
\label{thm:impl:efx-to-propavg}
Let $([n], [m], (v_i)_{i=1}^n, \eqEnt)$ be a fair division instance
where $v_i$ is submodular for some agent $i$ and $v_i(A_i) \ge 0$.
If an allocation $A$ is EFX-fair to agent $i$,
then it is also PROPavg-fair to agent $i$.
\end{lemma}
\begin{proof}
If $A$ is PROP-fair to agent $i$, we are done, so assume $A$ is not PROP-fair to $i$.
By \cref{thm:submod-marginal-is-submod}, we get that $v_i(\cdot \mid A_i)$ is subadditive.
Hence, $v_i([m]) = v_i(A_i) + v_i([m] \mid A_i) \le v_i(A_i) + \sum_{j \neq i} v_i(A_j \mid A_i)$.
Then for some agent $\jhat \in [n] \setminus \{i\}$, we have
\[ v_i(A_i) < \frac{v_i([m])}{n} < v_i(A_{\jhat} \mid A_i) \le v_i(A_{\jhat}). \]

Since $i$ doesn't EFX-envy $\jhat$, for all $S \subseteq A_i$ such that
$v_i(S \mid A_i \setminus S) < 0$, we get
\[ v_i(A_i \setminus S) \ge v_i(A_{\jhat}) > \frac{v_i([m])}{n}. \]
Hence, condition C2 of PROPavg is satisfied (c.f.~\cref{defn:propavg}).

For any $j \in [n] \setminus \{i\}$, recall that
$\tau_j \defeq 0$ if $v_i(S \mid A_i) \le 0$ for all $S \subseteq A_j$, and
$\tau_j \defeq \min(\{v_i(S \mid A_i): S \subseteq A_j \text{ and } v_i(S \mid A_i) > 0\})$ otherwise.
If $\tau_j = 0$, then $v_i(A_j \mid A_i) \le 0 \le v_i(A_i) + \tau_j$.
Now suppose $\tau_j > 0$. Then $\tau_j = v_i(S \mid A_i) > 0$ for some $S \subseteq A_j$.
Since $A$ is EFX-fair to $i$,
\begin{align*}
& v_i(A_i) + \tau_j
    = v_i(A_i) + v_i(S \mid A_i)
\\ &\ge v_i(A_j \setminus S) + v_i(S \mid A_i)
\\ &\ge v_i(A_j \setminus S \mid A_i) + v_i(S \mid A_i)
    \tag{$v_i$ is submodular}
\\ &\ge v_i(A_j \mid A_i).
    \tag{$v_i(\cdot \mid A_i)$ is subadditive}
\end{align*}
Let $T \defeq \{\tau_j: j \in [n] \setminus \{i\} \text{ and } \tau_j > 0\}$.
On adding the above inequalities for all $j \in [n] \setminus \{i\}$,
and using the subadditivity of $v_i(\cdot \mid A_i)$, we get
\begin{align*}
& (n-1)v_i(A_i) + \sum_{j \neq i}\tau_j
    \ge \sum_{j \neq i} v_i(A_j \mid A_i)
    \ge v_i([m] \setminus A_i \mid A_i)
\\ &\implies nv_i(A_i) + \Sum(T) \ge v_i([m]).
\end{align*}
If $T = \emptyset$, then condition C4 of PROPavg is trivially satisfied.
Otherwise, $v_i(A_i) + \Sum(T)/(n-1) > v_i(A_i) + \Sum(T)/n \ge v_i([m])/n$.
\end{proof}

\begin{lemma}[EFX $\fimplies$ PROPx for $n=2$]
\label{thm:impl:efx-to-propx-n2}
Let $([2], [m], (v_1, v_2), w)$ be a fair division instance
where $v_i$ is subadditive for some agent $i$.
If an allocation $A$ is EFX-fair to agent $i$,
then it is also PROPx-fair to agent $i$.
\end{lemma}
\begin{proof}
Let the two agents be $i$ and $j$.
If $A$ is PROP-fair to agent $i$, we are done, so assume $v_i(A_i) < w_iv_i([m])$.
By subadditivity of $v_i$, we get $v_i([m]) \le v_i(A_i) + v_i(A_j)$. Hence,
\[ \frac{v_i(A_i)}{w_i} < v_i([m]) < \frac{v_i(A_j)}{w_j}. \]
Hence, $i$ envies $j$.

Let $S \subseteq A_i$ such that $v_i(S \mid A_i \setminus S) < 0$.
Since $A$ is EFX-fair to $i$, we get
\[ \frac{v_i(A_i \setminus S)}{w_i} \ge \frac{v_i(A_j)}{w_j} > v_i([m]). \]

Let $S \subseteq A_j$ such that $v_i(S \mid A_i) > 0$. Then
\begin{align*}
v_i([m]) &\le v_i(A_i \cup S) + v_i(A_j \setminus S)
    \tag{$v_i$ is subadditive}
\\ &\le v_i(A_i \cup S) + \frac{w_j}{w_i}v_i(A_i)
    \tag{$A$ is EFX-fair to $i$}
\\ &< v_i(A_i \cup S) + \frac{w_j}{w_i}v_i(A_i \cup S)
    = \frac{v_i(A_i \cup S)}{w_i}.
\end{align*}

Hence, $A$ is PROPx-fair to $i$.
\end{proof}

\begin{lemma}[M1S $\fimplies$ PROPx for binary subadditive]
\label{thm:impl:m1s-to-propx-binary-subadd}
Let $([n], [m], (v_i)_{i=1}^n, \eqEnt)$ be a fair division instance
where $v_i$ is subadditive for some agent $i$ and $v_i$ has binary marginals,
i.e., $v_i(g \mid X) \in \{0, 1\}$ for all $X \subseteq [m]$ and $g \in [m] \setminus X$.
If an allocation $A$ is M1S-fair to agent $i$,
then it is also PROPx-fair to agent $i$.
\end{lemma}
\begin{proof}
Let $B$ be agent $i$'s M1S-certificate for $A$. Let $k \defeq v_i(B_i)$.
Then $v_i(A_i) \ge k$ and $B$ is EF1-fair to $i$.
Pick $j \in [n] \setminus \{i\}$. If $i$ doesn't envy $j$, then $v_i(B_j) \le k$.
Otherwise, $\exists g \in B_j$ such that $v_i(B_j \setminus \{g\}) \le k$.
So, $v_i(B_j) = v_i(B_j \setminus \{g\}) + v_i(g \mid B_j \setminus \{g\}) \le k + 1$.
Hence,
\[ v_i([m]) \le \sum_{j=1}^n v_i(B_j) \le k + (n-1)(k+1) = nk + (n-1). \]
Hence, agent $i$'s proportional share is at most $k + (1-1/n) < k + 1$.

If $v_i(A_i) \ge k + 1$, then $A$ is PROP-fair to $i$. So now assume $v_i(A_i) = k$.
Let $S \subseteq [m] \setminus A_i$ such that $v_i(S \mid A_i) > 0$.
Since marginals are binary, we have $v_i(A_i \cup S) \ge v_i(A_i) + 1 = k + 1$,
so $A$ is PROPx-fair to agent $i$.
\end{proof}

\subsection{MMS vs EFX}
\label{sec:impls-extra:mms-vs-efx}

We prove some results connecting MMS, EFX, and related notions,
using techniques from \cite{plaut2020almost,caragiannis2023new}.

\begin{lemma}
\label{thm:mms-and-all-envy}
For a fair division instance $([n], [m], (v_i)_{i=1}^n, w)$,
suppose an allocation $A$ is WMMS-fair to agent $i$
and $i$ envies every other agent.
Then $A$ is also EFX-fair to agent $i$ if at least one of these conditions hold:
\begin{tightenum}
\item The items are goods to agent $i$ (i.e., $v_i(g \mid R) \ge 0$
    for all $R \subseteq [m]$ and $g \in [m] \setminus R$).
\item $v_i$ is additive and $w_i \le w_j$ for all $j \in [n] \setminus \{i\}$.
\end{tightenum}
\end{lemma}
\begin{proof}
Suppose agent $i$ is not EFX-satisfied by $A$, i.e., she EFX-envies some agent $j$.
Then $\exists S \subseteq A_i \cup A_j$ where either

\begin{tightenum}
\item $S \subseteq A_j$, $v_i(S \mid A_i) > 0$, and
    $\displaystyle \frac{v_i(A_i)}{w_i} < \frac{v_i(A_j \setminus S)}{w_j}$.
\item $S \subseteq A_i$, $v_i(S \mid A_i \setminus S) < 0$, and
    $\displaystyle \frac{v_i(A_i \setminus S)}{w_i} < \frac{v_i(A_j)}{w_j}$.
\end{tightenum}

If all items are goods, case 2 doesn't occur.

\textbf{Case 1}: $S \subseteq A_j$

Let $B$ be the allocation obtained by transferring $S$ from $A_j$ to $A_i$.
Formally, let $B_i \defeq A_i \cup S$, $B_j \defeq A_j \setminus S$,
and $B_k \defeq A_k$ for all $k \in [n] \setminus \{i, j\}$. Then
\[ \frac{v_i(B_i)}{w_i} = \frac{v_i(A_i) + v_i(S \mid A_i)}{w_i} > \frac{v_i(A_i)}{w_i}, \]
\[ \frac{v_i(B_j)}{w_j} = \frac{v_i(A_j \setminus S)}{w_j} > \frac{v_i(A_i)}{w_i}, \]
and for any $k \in [n] \setminus \{i, j\}$, we get
\[ \frac{v_i(B_k)}{w_k} = \frac{v_i(A_k)}{w_k} > \frac{v_i(A_i)}{w_i}. \]
Hence,
\[ \min_{k=1}^n \frac{v_i(B_k)}{w_k} > \frac{v_i(A_i)}{w_i} \ge \frac{\WMMS_i}{w_i}, \]
which is a contradiction.

\textbf{Case 2}: $S \subseteq A_i$

Let $v_i$ be additive and $w_i \le w_j$.
Let $B$ be the allocation obtained by transferring $S$ from $A_i$ to $A_j$. Formally,
let $B_i \defeq A_i \setminus S$, $B_j \defeq A_j \cup S$,
and $B_k \defeq A_k$ for all $k \in [n] \setminus \{i, j\}$. Then
\[ \frac{v_i(B_i)}{w_i} = \frac{v_i(A_i) - v_i(S)}{w_i} > \frac{v_i(A_i)}{w_i}, \]
\[ \frac{v_i(B_j)}{w_j} = \frac{v_i(A_j) + v_i(S)}{w_j} > \frac{v_i(A_i \setminus S)}{w_i} - \frac{(-v_i(S))}{w_j} \ge \frac{v_i(A_i)}{w_i}, \]
and for any $k \in [n] \setminus \{i, j\}$, we get
\[ \frac{v_i(B_k)}{w_k} = \frac{v_i(A_k)}{w_k} > \frac{v_i(A_i)}{w_i}. \]
Hence,
\[ \min_{k=1}^n \frac{v_i(B_k)}{w_k} > \frac{v_i(A_i)}{w_i} \ge \frac{\WMMS_i}{w_i}, \]
which is a contradiction.
\end{proof}

\begin{lemma}[MMS $\fimplies$ EFX for $n=2$]
\label{thm:impl:mms-to-efx-n2}
For a fair division instance $([2], [m], (v_i)_{i=1}^2, w)$,
suppose an allocation $A$ is WMMS-fair to agent 1.
Then $A$ is also EFX-fair to agent 1 if at least one of these conditions hold:
\begin{tightenum}
\item The items are goods to agent 1.
\item $v_1$ is additive and $w_1 \le w_2$.
\end{tightenum}
\end{lemma}
\begin{proof}
If agent 1 doesn't envy agent 2, she is EFX-satisfied.
Otherwise, she is EFX-satisfied because of \cref{thm:mms-and-all-envy}.
\end{proof}

Theorem 2 in \cite{caragiannis2023new} states that an MMS allocation is also an EEFX allocation
(for additive valuations over goods and equal entitlements).
The proof can be easily adapted to non-additive valuations over goods and unequal entitlements.
For the sake of completeness, we give a proof below.

\begin{lemma}[MMS $\fimplies$ EEFX, \cite{caragiannis2023new}]
\label{thm:impl:mms-to-eefx}
For a fair division instance $([n], [m], (v_i)_{i=1}^n, w)$,
if all items are goods to agent $i$ and allocation $A$ is WMMS-fair to agent $i$,
then $A$ is also epistemic-EFX-fair to $i$.
\end{lemma}
\begin{proof}
In any allocation $X$, let
$E_X$ be the set of agents envied by $i$,
$S_X$ be the set of agents EFX-envied by $i$,
$W_X$ be the total number of items among the agents in $S_X$.

$E_X \defeq \{t \in [n] \setminus \{i\}: i \textrm{ envies } t \textrm{ in } X\}$,
$S_X \defeq \{t \in [n] \setminus \{i\}: i \textrm{ EFX-envies } t \textrm{ in } X\}$,
$W_X \defeq \sum_{t \in S_X} |X_t|$, and $\phi(X) \defeq (-|E_X|, W_X)$.

First, we show that for any allocation $X$ where $|E_X| \le n-2$ and $S_X \neq \emptyset$,
there exists a \emph{better} allocation $Y$, i.e, $Y_i = X_i$ and $\phi(Y) < \phi(X)$
(tuples are compared lexicographically).

Let $j \in S_X$ and $k \in [n] \setminus \{i\} \setminus E_X$.
Since $i$ EFX-envies $j$, $\exists S \subseteq X_j$ such that $v_i(S \mid X_i) > 0$ and
\[ \frac{v_1(X_1)}{w_1} < \frac{v_1(X_j \setminus S)}{w_j}. \]
Let $Y_k \defeq X_k \cup S$, $Y_j \defeq X_j \setminus S$,
and $Y_t \defeq X_t$ for all $t \in [n] \setminus \{j, k\}$.

Then $i$ envies $j$ in $Y$. Hence, $E_X \subseteq E_Y$.
If $k \in E_Y$, then $|E_Y| > |E_X|$, so $\phi(Y) < \phi(X)$.
If $k \not\in E_Y$, then $W_Y < W_X$, so $\phi(Y) < \phi(X)$.
Hence, $Y$ is better than $X$.

Set $X = A$. As long as $|E_X| < n-1$ and $S_X \neq \emptyset$,
keep modifying $X$ as per Lemma 1.
This process will eventually end, since $\phi(X)$ keeps reducing,
and there are a finite number of different values $\phi(X)$ can take.
Let $B$ be the final allocation thus obtained.
Then $B_i = A_i$, and $|E_B| = n-1$ or $S_B = \emptyset$.

By \cref{thm:mms-and-all-envy},
$|E_B| = n-1$ implies $S_B = \emptyset$.
Hence, $B$ is agent $i$'s EEFX-certificate for $A$.
\end{proof}

\begin{definition}
\label{defn:leximin}
Let $R$ be a totally-ordered set.
For any sequence $X = (x_i)_{i=1}^n$ from $R$, define $\sorted(X)$ to be a permutation of $X$
where entries occur in non-decreasing order.
For any two sequences $X = (x_i)_{i=1}^n$ and $Y = (y_i)_{i=1}^n$ from $R$, we say that $X \le Y$ if
$\exists i \in [n]$ such that $x_i \le y_i$ and $x_j = y_j$ for all $j \in [i-1]$.
(Note that this relation $\le$ over sequences is a total ordering.)

For any set $S \subseteq M$, let $\Pi_n(S)$ denote the set of all $n$-partitions of $S$.
We say that $P \in \Pi_n([m])$ is a leximin $n$-partition of a function $f: 2^{[m]} \to R$ if
\[ P \in \argmax_{X \in \Pi_n([m])} \sorted\left((f(X_j))_{j=1}^n\right). \]
\end{definition}

It is easy to see that if $P$ is a leximin $n$-partition of $f: 2^{[m]} \to \mathbb{R}$,
then $\min_{j=1}^n f(P_j) = \MMS_f^n([m])$.

\begin{lemma}[MMS $\fimplies$ MXS]
\label{thm:impl:mms-to-mxs}
Let $\Ical \defeq ([n], [m], (v_i)_{i=1}^n, \eqEnt)$ be a fair division instance.
Let allocation $A$ be MMS-fair to agent $i$.
Then $A$ is also MXS-fair to $i$ if at least one of these conditions hold:
\begin{tightenum}
\item All items are goods to agent $i$.
\item $v_i$ is additive.
\end{tightenum}
\end{lemma}
\begin{proof}
We will show that agent $i$'s leximin $n$-partition is her MXS-certificate for $A$,
which would prove that $A$ is MXS-fair to agent $i$.

Without loss of generality, assume $i = 1$.
Let $P$ be a leximin $n$-partition of $v_1$ (c.f.~\cref{defn:leximin})
such that $v_1(P_1) \le v_1(P_2) \le \ldots \le v_1(P_n)$.
Then $v_1(P_1) = \MMS_{v_1}^n([m]) \le v_1(A_1)$.

For any agent $j \ge 2$, the allocation $(P_1, P_j)$ is leximin for
the instance $\Icalhat \defeq (\{i, j\}, P_1 \cup P_j, (v_1, v_j), (1/2, 1/2))$.
Hence, agent 1 is MMS-satisfied by $(P_1, P_j)$ in $\Icalhat$.
Since either all items are goods to agent 1 or $v_1$ is additive,
by \cref{thm:impl:mms-to-efx-n2}, agent 1 is EFX-satisfied by $(P_1, P_j)$ in $\Icalhat$.

On considering all values of $j$, we get that agent 1 is EFX-satisfied by $P$ in $\Ical$.
Hence, $P$ is agent 1's MXS-certificate for $A$.
\end{proof}

\begin{lemma}[MMS $\fimplies$ \MXSZero]
\label{thm:impl:mms-to-mxs0}
Let $\Ical \defeq ([n], [m], (v_i)_{i=1}^n, \eqEnt)$ be a fair division instance over goods.
If an allocation $A$ is MMS-fair to agent $i$, then it is also \MXSZero-fair to $i$.
(\EFXZero{} for goods is defined in \cref{defn:efx0-goods}.
\MXSZero{} is the minimum-\EFXZero{}-share.
Also note that \EFXZero{} implies EF1, and so, \MXSZero{} implies M1S.)
\end{lemma}
\begin{proof}
Without loss of generality, assume $i = 1$.
Let $\vhat(X) \defeq (v_1(X), |X|)$.
Then $\vhat$'s co-domain is totally-ordered, assuming pairs are compared lexicographically.
Let $P$ be a leximin $n$-partition of $\vhat$ (c.f.~\cref{defn:leximin})
such that $\vhat(P_1) \le \vhat(P_2) \le \ldots \le \vhat(P_n)$.
($P$ is also called the leximin++ partition of $v_1$ \cite{plaut2020almost}).
Then $v_1(P_1) = \min_{j=1}^n v_1(P_j)$.
Hence, $v_1(P_1) = \MMS_{v_1}^n([m]) \le v_1(A_1)$.

For any $j \ge 2$, we get that $(P_1, P_j)$ is also a leximin 2-partition of $\vhat$
(when $\vhat$'s domain is restricted to $P_1 \cup P_j$).
We will now show that agent 1 doesn't \EFXZero{}-envy agent $j$, i.e.,
$v_1(P_1) \ge \max_{g \in P_j} v_1(P_j \setminus \{g\})$.
(If $P_j = \emptyset$, this is trivially true.)
Suppose $v_1(P_1) < v_1(P_j \setminus \{g\})$ for some $g \in P_j$.
Let $Q_1 \defeq P_1 \cup \{g\}$ and $Q_j \defeq P_j \setminus \{g\}$.
Then $\vhat(Q_1) > \vhat(P_1)$ and $\vhat(Q_j) > \vhat(P_1)$.
Hence, $(P_1, P_j)$ is not a leximin 2-partition of $\vhat$, which is a contradiction.
Hence, agent 1 doesn't \EFXZero{}-envy agent $j$.

On considering all values of $j$, we get that agent 1 is \EFXZero-satisfied by $P$ in $\Ical$.
Hence, $P$ is agent 1's \MXSZero{}-certificate for $A$.
\end{proof}

\subsection{Among PROP, APS, MMS}

We prove implications among share-based notions like PROP, APS, and MMS.

\begin{lemma}[PROP $\fimplies$ APS, Proposition 4 of \cite{babaioff2023fair}]
\label{thm:impl:prop-to-aps}
For any fair division instance
\\ $([n], [m], (v_i)_{i=1}^n, w)$,
$\APS_i \le w_iv_i([m])$ for agent $i$ if $v_i$ is additive.
\end{lemma}
\begin{proof}
Set the price $p(g)$ of each item $g$ to $v_i(g)$. Then
\[ \APS_i \le \max_{S \subseteq [m]: p(S) \le w_ip([m])} v_i(S)
= \max_{S \subseteq [m]: v_i(S) \le w_iv_i([m])} v_i(S) \le w_iv_i([m]).
\qedhere \]
\end{proof}

\begin{lemma}[PROP $\fimplies$ WMMS]
\label{thm:impl:prop-to-wmms}
For any fair division instance $([n], [m], (v_i)_{i=1}^n, w)$,
if $v_i$ is superadditive, then $\WMMS_i \le w_iv_i([m])$.
\end{lemma}
\begin{proof}
Let $P$ be agent $i$'s WMMS partition. Then
\[ v_i([m]) \ge \sum_{j=1}^n v_i(P_j) = \sum_{j=1}^n w_j\left(\frac{v_i(P_j)}{w_j}\right)
    \ge \sum_{j=1}^n w_j\frac{\WMMS_i}{w_i} = \frac{\WMMS_i}{w_i}. \qedhere \]
\end{proof}

\begin{lemma}
\label{thm:prefix-sum-bound}
Let $a_1 \le a_2 \le \ldots \le a_n$ be $n$ real numbers.
Let $s_k \defeq \sum_{i=1}^k a_i$ for any $0 \le k \le n$.
Then $s_k \le (k/n)s_n$.
\end{lemma}
\begin{proof}
$\displaystyle s_n = s_k + \sum_{i=k+1}^n a_i \ge s_k + (n-k)a_k \ge s_k + (n-k)\frac{s_k}{k}
= \frac{n}{k}s_k$.
\end{proof}

\begin{lemma}[PROP $\fimplies$ pessShare]
\label{thm:impl:prop-to-pessShare}
For any fair division instance $([n], [m], (v_i)_{i=1}^n, w)$,
if $v_i$ is superadditive, then $\pessShare_i \le w_iv_i([m])$.
\end{lemma}
\begin{proof}
Let $P$ be agent $i$'s $\ell$-out-of-$d$-partition.
Assume \wLoG{} that $v_i(P_1) \le v_i(P_2) \le \ldots \le v_i(P_d)$.
Then by \cref{thm:prefix-sum-bound} and superadditivity of $v_i$, we get
\[ \loodM_i = \sum_{j=1}^{\ell} v_i(P_j)
    \le \frac{\ell}{d}\sum_{j=1}^d v_i(P_j) \le \frac{\ell}{d}v_i([m]). \]
Hence,
\[ \pessShare_i \defeq \sup_{1 \le \ell \le d: \ell/d \le w_i} \loodM_i
    \le \sup_{1 \le \ell \le d: \ell/d \le w_i} (\ell/d)v_i([m]) \le w_iv_i([m]).
    \qedhere \]
\end{proof}

\begin{lemma}[APS $\fimplies$ pessShare]
\label{thm:impl:aps-to-pess}
For any fair division instance $([n], [m], (v_i)_{i=1}^n, w)$,
$\APS_i \ge \pessShare_i$ for every agent $i$.
\end{lemma}
\begin{proof}
Proposition 2 in \cite{babaioff2023fair} proves this for goods,
but their proof works for mixed manna too.
\end{proof}

\begin{lemma}
\label{thm:wmms-vs-knapsack}
For a fair division instance $([n], [m], (v_i)_{i=1}^n, w)$ and any agent $i$, define
\[ \beta_i \defeq \max_{j=1}^n \max_{\substack{S \subseteq [m]:\\v_i(S) \le w_jv_i([m])}} \frac{v_i(S)}{w_j}. \]
If $v_i$ is superadditive, then $\WMMS_i \le w_i\beta_i$.
If $v_i$ is additive and $n = 2$, then $\WMMS_i = w_i\beta_i$.
\end{lemma}
\begin{proof}
For any $j \in [n]$, define
\[ S_j \defeq \argmax_{\substack{S \subseteq [m]:\\v_i(S) \le w_jv_i([m])}} \frac{v_i(S)}{w_j}. \]
Then $\beta_i \defeq \max_{j=1}^n v_i(S_j)/w_j$.

Let $\Pi_n([m])$ be the set of all $n$-partitions of $[m]$. Let
\begin{align*}
P &\defeq \argmax_{P \in \Pi_n([m])} \min_{j=1}^n \frac{v_i(P_j)}{w_j},
& k &\defeq \argmin_{j=1}^n \frac{v_i(P_j)}{w_j}.
\end{align*}
Then $\WMMS_i/w_i \defeq v_i(P_k)/w_k$.

By \cref{thm:impl:prop-to-wmms}, we get $v_i(P_k)/w_k \le v_i([m])$. Hence,
\[ \frac{\WMMS_i}{w_i} = \frac{v_i(P_k)}{w_k} \le \frac{v_i(S_k)}{w_k}
    \le \max_{j=1}^n \frac{v_i(S_j)}{w_j} = \beta_i. \]

Now let $v_i$ be additive and $n = 2$.
For any $j \in [2]$, let $Q^{(j)}$ be an allocation where $Q^{(j)}_j \defeq S_j$
and $Q^{(j)}_{3-j} \defeq [m] \setminus S_j$.
Then $v_i(Q^{(j)}_j) = v_i(S_j) \le w_jv_i([m])$ and
\[ v_i(Q^{(j)}_{3-j}) = v_i([m]) - v_i(S_j) \ge v_i([m]) - w_jv_i([m]) = w_{3-j}v_i([m]). \]
Hence,
\[ \frac{v_i(Q^{(j)}_j)}{w_j} \le v_i([m]) \le \frac{v_i(Q^{(j)}_{3-j})}{w_{3-j}}. \]
Therefore,
\begin{align*}
\frac{\WMMS_i}{w_i} &= \min\left(\frac{v_i(P_1)}{w_1}, \frac{v_i(P_2)}{w_2}\right)
\\ &\ge \max_{j=1}^n \min\left(\frac{v_i(Q^{(j)}_j)}{w_j}, \frac{v_i(Q^{(j)}_{3-j})}{w_{3-j}}\right)
    \tag{by definition of $P$}
\\ &= \max_{j=1}^n \frac{v_i(S_j)}{w_j} = \beta_i.
\end{align*}
Hence, $\WMMS_i/w_i \ge \beta_i$.
\end{proof}

\begin{lemma}[WMMS $\fimplies$ APS for $n=2$]
\label{thm:impl:mms-to-aps-n2}
For a fair division instance $([2], [m], (v_i)_{i=1}^2, w)$,
if $v_i$ is additive for some $i$, then $\APS_i \le \WMMS_i$.
Moreover, when entitlements are equal, we get $\APS_i = \MMS_i$.
\end{lemma}
\begin{proof}
By \cref{thm:wmms-vs-knapsack}, we get
\[ \frac{\WMMS_i}{w_i} = \beta_i \defeq \max_{j=1}^2 \frac{v_i(S_j)}{w_j},
\quad\textrm{where}\quad
S_j \defeq \argmax_{\substack{S \subseteq [m]:\\ v_i(S) \le w_jv_i([m])}} v_i(S). \]
On setting $p = v_i$ in the primal definition of APS (\cref{defn:aps}), we get
\[ \APS_i \le \max_{\substack{S \subseteq [m]:\\ p(S) \le w_ip([m])}} v_i(S)
    = v_i(S_i) \le w_i\beta_i = \WMMS_i. \]
When entitlements are equal, $\APS_i \ge \pessShare_i \ge \MMS_i$
by \cref{thm:impl:aps-to-pess}.
\end{proof}

\begin{lemma}[MMS = APS, \cite{kulkarni2024approximating}]
\label{thm:impl:mms-to-aps-matroid}
For a fair division instance $([n], [m], (v_i)_{i=1}^n, \eqEnt)$,
if $v_i$ is submodular for some agent $i$, and $v_i$ has binary marginals
(i.e., $v_i(g \mid X) \in \{0, 1\}$ for some $X \subseteq [m]$ and $g \in [m] \setminus X$),
then $\APS_i = \MMS_i$.
\end{lemma}

\subsection{Additive Triboolean Valuations}
\label{sec:impls-extra:tribool}

\begin{table*}[htb]
\centering
\caption[Tribool implications]{Implications among fairness notions when
valuations are additive and marginals are triboolean,
i.e, they belong to the set $\{-1, 0, 1\}$.}
\label{table:impls-tribool}
\small
\begin{tabular}{cccccccc}
\toprule & \footnotesize valuations & \footnotesize marginals & \footnotesize $n=2$ & \footnotesize entitlements & &
\\\midrule EF1 $\fimplies$ EFX & additive & $\{-1, 0, 1\}$
    & -- & -- & -- & trivial
\\[\defaultaddspace] EEF1 $\fimplies$ EEFX & additive & $\{-1, 0, 1\}$
    & -- & -- & -- & trivial
\\[\defaultaddspace] M1S $\fimplies$ MXS & additive & $\{-1, 0, 1\}$
    & -- & -- & -- & trivial
\\[\defaultaddspace] PROP1 $\fimplies$ PROPx & -- & $\{-1, 0, 1\}$
    & -- & -- & \cref{thm:impl:prop1-to-propx-tribool} & \textbf{new}
%
\\\midrule PROP $\fimplies$ EEF & additive & $\{-1, 0, 1\}$
    & -- & equal & \cref{thm:impl:tribool:prop} & \textbf{new}
\\[\defaultaddspace] APS $\fimplies$ PROPx & additive & $\{-1, 0, 1\}$
    & -- & -- & \cref{thm:impl:tribool:prop1,thm:impl:tribool:aps} & \textbf{new}
\\[\defaultaddspace] PROP1 $\fimplies$ APS & additive & $\{-1, 0, 1\}$
    & -- & -- & \cref{thm:impl:tribool:prop1,thm:impl:tribool:aps} & \textbf{new}
\\[\defaultaddspace] M1S $\fimplies$ APS & additive & $\{-1, 0, 1\}$
    & -- & equal & \cref{thm:impl:tribool:aps,thm:impl:tribool:m1s} & \textbf{new}
\\[\defaultaddspace] MMS $\fimplies$ EEFX & additive & $\{-1, 0, 1\}$
    & -- & equal & \cref{thm:impl:tribool:mms-to-eefx} & \textbf{new}
%
\\\midrule EF1 $\fimplies$ GAPS & additive & $\{-1, 0, 1\}$
    & -- & equal & \cref{thm:impl:tribool:ef1-gaps} & \textbf{new}
\\[\defaultaddspace] EF1 $\fimplies$ GAPS & additive & $\{-1, 0, 1\}$
    & $n=2$ & -- & \cref{thm:impl:tribool:ef1-gaps} & \textbf{new}
\\[\defaultaddspace] EF1 $\fimplies$ GAPS & additive & $\{-1, 0\}$
    & -- & -- & \cref{thm:impl:tribool:ef1-gaps} & \textbf{new}
\\ \bottomrule
\end{tabular}
\end{table*}

\begin{lemma}[PROP1 $\fimplies$ PROPx]
\label{thm:impl:prop1-to-propx-tribool}
Consider a fair division instance $([n], [m], (v_i)_{i=1}^n, w)$ where for some agent $i$,
marginals are triboolean, i.e., $v_i(t \mid S) \in \{-1, 0, 1\}$
for all $S \subseteq [m]$ and $t \in [m] \setminus S$ for some agent $i$.
Then if an allocation $A$ is PROP1-fair to agent $i$, then it is also PROPx-fair to $i$.
\end{lemma}
\begin{proof}
If $v_i(A_i) \ge w_iv_i([m])$, then $A$ is PROPx.
Otherwise, we get $v_i(A_i) + 1 > w_iv_i([m])$ since $A$ is PROP1
and marginals are triboolean.
Removing any positive-disutility subset from $A_i$
or adding any positive-utility subset to $A_i$ will increase its value by at least 1.
Hence, $A$ is PROPx.
\end{proof}

\begin{lemma}
\label{thm:tribool-rr}
For an additive function $f: 2^{[m]} \to \{-1, 0, 1\}$,
there exists an $n$-partition $P$ such that $|f(P_i) - f(P_j)| \le 1$
for all $i, j \in [n]$ and
and $\floor{f([m])/n} \le f(P_i) \le \ceil{f([m])/n}$ for all $i \in [n]$.
\end{lemma}
\begin{proof}
Partition $[m]$ into
goods $M_+ \defeq \{g \in [m]: v_i(g) > 0\}$,
chores $M_- \defeq \{c \in [m]: v_i(c) < 0\}$,
and neutral items $M_0 \defeq \{t \in [m]: v_i(t) = 0\}$.
Fuse items $M_0$, $\min(|M_+|, |M_-|)$ goods, and $\min(|M_+|, |M_-|)$ chores
into a single item $h$.
Then we are left with only goods and a neutral item,
or only chores and a neutral item.
Using round-robin, one can allocate items such that
any two bundles differ by at most one item.
\end{proof}

\begin{lemma}
\label{thm:impl:tribool:prop}
Consider a fair division instance $([n], [m], (v_i)_{i=1}^n, \eqEnt)$
where $v_i$ is additive and $v_i(t) \in \{-1, 0, 1\}$ for all $t \in [m]$ for some agent $i$.
If an allocation $A$ is PROP-fair to $i$, then it is also epistemic-EF-fair to $i$.
\end{lemma}
\begin{proof}
Since $A$ is PROP-fair to $i$, and $v_i(S) \in \mathbb{Z}$ for all $S \subseteq [m]$,
we get $v_i(A_i) \ge \ceil{v_i([m])/n}$.

Construct an allocation $B$ where $B_i = A_i$, and items $[m] \setminus A_i$
are allocated among agents $[n] \setminus \{i\}$ using \cref{thm:tribool-rr} with $f = v_i$.
We will show that $B$ is agent $i$'s epistemic-EF-certificate for $A$.

In $B$, for each agent $j \in [n] \setminus \{i\}$, we have
\[ v_i(B_j) \le \bigceil{\frac{v_i([m] \setminus A_i)}{n-1}}
    \le \bigceil{\frac{v_i([m]) - v_i([m])/n}{n-1}}
    \le \bigceil{\frac{v_i([m])}{n}} \le v_i(A_i). \]
Hence, $i$ doesn't envy anyone in $B$.
Hence, $B$ is agent $i$'s epistemic-EF-certificate for $A$.
\end{proof}

\begin{lemma}
\label{thm:impl:tribool:prop1}
Consider a fair division instance $([n], [m], (v_i)_{i=1}^n, w)$ where
$v_i$ is additive and $v_i(t) \in \{-1, 0, 1\}$ for all $t \in [m]$ for some agent $i$.
Then the following statements are equivalent:
\begin{tightenum}
\item Allocation $A$ is PROP1-fair to $i$.
\item Allocation $A$ is PROPx-fair to $i$.
\item $v_i(A_i) \ge \floor{w_iv_i([m])}$.
\end{tightenum}
\end{lemma}
\begin{proof}
Partition $[m]$ into
goods $M_+ \defeq \{g \in [m]: v_i(g) > 0\}$,
chores $M_- \defeq \{c \in [m]: v_i(c) < 0\}$,
and neutral items $M_0 \defeq \{t \in [m]: v_i(t) = 0\}$.

\textbf{Case 1}: $A_i$ has all goods and no chores.
\\ Then $v_i(A_i) \ge \max(0, v_i([m]))$.
If $v_i([m]) \ge 0$, then $v_i(A_i) \ge v_i([m]) \ge w_iv_i([m])$,
else $v_i(A_i) \ge 0 \ge w_iv_i([m])$.
Hence, $v_i(A_i) \ge w_iv_i([m])$ and $A$ is PROPx+PROP1.

\textbf{Case 2}: $A_i$ has a chore or some good is outside $A_i$.
\\ Then adding a good to $A_i$ or removing a chore from $A_i$
makes it's value more than $w_iv_i([m])$ iff $v_i(A_i) \ge \floor{w_iv_i([m])}$.
Hence, $A$ is PROP1 iff $A$ is PROPx iff $v_i(A_i) \ge \floor{w_iv_i([m])}$.
\end{proof}

\begin{lemma}
\label{thm:impl:tribool:aps}
Consider a fair division instance $([n], [m], (v_i)_{i=1}^n, w)$ where
$v_i$ is additive and $v_i(t) \in \{-1, 0, 1\}$ for all $t \in [m]$ for some agent $i$.
Then $\APS_i = \floor{w_iv_i([m])}$.
\end{lemma}
\begin{proof}
Partition $[m]$ into goods $M_+ \defeq \{g \in [m]: v_i(g) > 0\}$,
chores $M_- \defeq \{c \in [m]: v_i(c) < 0\}$, and
neutral items $M_0 \defeq \{t \in [m]: v_i(t) = 0\}$.

First, set $p(t) = v_i(t)$ for each $t \in [m]$ to get $\APS_i \le w_im_i$.
Since the APS is the value of some bundle, and bundle values can only be integers,
we get $\APS_i \le \floor{w_im_i}$.

Pick an arbitrary price vector $p \in \Delta_m$.
We will construct a set $S$ such that $p(S) \le w_ip([m])$ and $v_i(S) \ge w_iv_i([m])$.
Fuse items $M_0$, $\min(|M_+|, |M_-|)$ goods, and $\min(|M_+|, |M_-|)$ chores
into a single item $h$.
Let $M'_+$ and $M'_-$ be the remaining goods and chores, respectively.
Then $M'_+ = \emptyset$ or $M'_- = \emptyset$.
Using techniques from \cref{thm:aps-optimal-price},
we can assume \wLoG{} that $p_g \ge 0$ for all $g \in M'_+$,
$p_c \le 0$ for all $c \in M'_-$, and $p_h = 0$.

\textbf{Case 1}: $M'_- = \emptyset$.
\\ Let $m_i \defeq |M'_+| = v_i([m])$.
Let $S$ be the cheapest $\floor{w_im_i}$ items in $M'_+$.
Then using \cref{thm:prefix-sum-bound}, we get
\[ p(S) \le \frac{\floor{w_im_i}}{m_i}p(M_+) \le w_ip([m]). \]
Then $S$ is affordable and $v_i(S) = \floor{w_im_i}$.
Hence, $\APS_i \ge \floor{w_im_i}$.

\textbf{Case 2}: $M'_+ = \emptyset$.
\\ Let $m_i \defeq |M'_-| = -v_i([m])$.
Let $S$ be the cheapest $\ceil{w_im_i}$ items in $M'_- \cup \{h\}$.
Then using \cref{thm:prefix-sum-bound}, we get
\[ -p(S) \ge \frac{\ceil{w_im_i}}{m_i}(-p([m])) \ge w_i(-p([m])). \]
Then $S$ is affordable and $-v_i(S) \le \ceil{w_im_i} = -\floor{w_iv_i([m])}$.
Hence, $\APS_i \ge \floor{w_iv_i([m])}$.
\end{proof}

\begin{lemma}
\label{thm:impl:tribool:m1s}
Consider a fair division instance $([n], [m], (v_i)_{i=1}^n, \eqEnt)$
where $v_i$ is additive and $v_i(t) \in \{-1, 0, 1\}$ for all $t \in [m]$ for some agent $i$.
Then $\MMS_i = \mathrm{M1S}_i = \floor{v_i([m])/n}$.
\end{lemma}
\begin{proof}
Allocate items $[m]$ among agents $[n]$ using \cref{thm:tribool-rr} with $f = v_i$.
Then any two bundles differ by a value of at most one.
Hence, $\MMS_i = \floor{m'/n}$ and $\mathrm{M1S}_i \le \floor{m'/n}$,
where $m' \defeq v_i([m])$.

Let $X$ be an allocation where agent $i$ is EF1-satisfied.
Then any two bundles can differ by a value of at most one.
Hence, the smallest value $v_i(X_i)$ can have is $\floor{m'/n}$.
Hence, $\mathrm{M1S}_i \ge \floor{m'/n}$.
\end{proof}

\begin{lemma}
\label{thm:impl:tribool:ef1-gaps}
Consider a fair division instance $([n], [m], (v_i)_{i=1}^n, w)$ where
$v_i$ is additive and $v_i(t) \in \{-1, 0, 1\}$ for all $t \in [m]$ for some agent $i$.
If an allocation $A$ is EF1-fair to $i$, then it is also groupwise-APS-fair to $i$
if at least one of these conditions hold:
\begin{tightenum}
\item $n=2$
\item $w_i \le w_j$ for all $j \in [n] \setminus \{i\}$.
\item $v_i(c) \in \{0, -1\}$ for all $c \in [m]$.
\end{tightenum}
\end{lemma}
\begin{proof}
Consider any subset $S$ of agents.
On restricting $A$ to $S$, we get an allocation $B$ that is EF1-fair to $i$.
$B$ is also PROP1-fair to $i$ by \cref{thm:impl:eef1-to-prop1-chores,thm:impl:eef1-to-prop1-submod,thm:impl:ef1-to-prop1-n2},
and APS-fair to $i$ by \cref{thm:impl:tribool:prop1,thm:impl:tribool:aps}.
Hence, $A$ is groupwise-APS-fair to $i$.
\end{proof}

\begin{remark}
\label{thm:ceil-floor}
For any $m \in \mathbb{Z}$ and $n \in \mathbb{Z}_{\ge 1}$, we get
\[ \bigfloor{\frac{m}{n}} = \bigceil{\frac{m+1}{n}} - 1. \]
\end{remark}

\begin{lemma}
\label{thm:impl:tribool:mms-to-eefx}
Consider a fair division instance $([n], [m], (v_i)_{i=1}^n, \eqEnt)$
where $v_i$ is additive and $v_i(t) \in \{-1, 0, 1\}$ for all $t \in [m]$ for some agent $i$.
If $v_i(A_i) \ge \floor{v_i([m])/n}$ for some allocation $A$,
then $A$ is epistemic-EFX-fair to $i$.
\end{lemma}
\begin{proof}
Construct an allocation $B$ where $B_i = A_i$, and items $[m] \setminus A_i$
are allocated among agents $[n] \setminus \{i\}$ using \cref{thm:tribool-rr} with $f = v_i$.
We will show that $B$ is agent $i$'s epistemic-EFX-certificate for $A$.

Let $k \defeq v_i([m])$.
Suppose $v_i(A_i) \ge \floor{k/n} = \ceil{(k+1)/n} - 1$ (c.f.~\cref{thm:ceil-floor}).
Then for any other agent $j \in [n] \setminus \{i\}$, we get
\[ v_i(B_j) \le \bigceil{\frac{v_i([m] \setminus A_i)}{n-1}}
    \le \bigceil{\frac{k - (k+1)/n + 1}{n-1}} = \bigceil{\frac{k+1}{n}}
    \le v_i(B_i) + 1. \]
If $B_j$ contains no goods and $B_i$ contains no chores,
then $v_i(B_i) \ge 0 \ge v_i(B_j)$, so $i$ doesn't envy $j$ in $B$.
Otherwise, transferring a good from $j$ to $i$ or a chore from $i$ to $j$ in $B$
eliminates $i$'s envy towards $j$.
Hence, $B$ is agent $i$'s epistemic-EFX-certificate for $A$.
\end{proof}

\subsection{Unit-Demand Valuations}
\label{sec:impls-extra:unit-demand}

We now study implications between fairness notions when agents have unit-demand valuations over goods.
A function $v: 2^{[m]} \to \mathbb{R}_{\ge 0}$ is said to be \emph{unit-demand} if $v(\emptyset) = 0$,
and for any non-empty set $X \subseteq M$, we have $v(X) = \max_{g \in X} v(\{g\})$.

Unit-demand functions capture scenarios where agents want just one good, e.g., when the goods are houses.
Unit-demand functions are known to be submodular and cancelable.
% TODO: prove it

\begin{table*}[htb]
\centering
\caption[Unit-demand implications]{Implications among fairness notions when
valuations are unit-demand, marginals are non-negative, and entitlements are equal.}
\label{table:impls-unit-demand}
\small
\begin{tabular}{ccHHHcH}
\toprule implication & \footnotesize valuations & \footnotesize marginals & \footnotesize $n=2$ & \footnotesize entitlements & proof &
\\\midrule MEFS $\fimplies$ EF
    & unit-demand & $\ge 0$ & -- & equal
    & \cref{thm:ud:ef} & trivial
\\[\defaultaddspace] MMS $\fimplies$ APS
    & unit-demand & $\ge 0$ & -- & equal
    & \cref{thm:ud:mms,thm:ud:aps} & \textbf{new}
\\[\defaultaddspace] PMMS $\fimplies$ PAPS
    & unit-demand & $\ge 0$ & -- & equal
    & \cref{thm:ud:mms,thm:ud:aps} & \textbf{new}
\\[\defaultaddspace] GMMS $\fimplies$ GAPS
    & unit-demand & $\ge 0$ & -- & equal
    & \cref{thm:ud:mms,thm:ud:aps} & \textbf{new}
\\[\defaultaddspace] M1S $\fimplies$ APS
    & unit-demand & $\ge 0$ & -- & equal
    & \cref{thm:ud:m1s,thm:ud:aps} & \textbf{new}
\\[\defaultaddspace] EF1 $\fimplies$ GAPS
    & unit-demand & $\ge 0$ & -- & equal
    & \cref{thm:ud:m1s,thm:ud:aps} & \textbf{new}
\\ \bottomrule
\end{tabular}
\end{table*}

\begin{remark}
\label{thm:ud:ef}
Consider a fair division instance $([n], [m], (v_i)_{i=1}^n, \eqEnt)$ over goods
where $v_i$ is unit-demand for some agent $i$.
\WLoG, let $v_i(1) \ge v_i(2) \ge \ldots \ge v_i(m)$.
Then agent $i$ is envy-free in allocation $A$ iff $v_i(A_i) = v(1)$.
\end{remark}

\begin{lemma}
\label{thm:ud:m1s}
Consider a fair division instance $([n], [m], (v_i)_{i=1}^n, \eqEnt)$ over goods
where $v_i$ is unit-demand for some agent $i$.
\WLoG, let $v_i(1) \ge \ldots \ge v_i(m)$.
Then allocation $A$ is M1S-fair to agent $i$ iff $v_i(A_i) \ge v_i(n)$.
\end{lemma}
\begin{proof}
Suppose $A$ is M1S-fair to agent $i$. Let $B$ be agent $i$'s M1S-certificate for $A$.
Let $G \defeq \{g \in [m]: v_i(g) > v_i(B_i)\}$.
Then $B$ is EF1-fair to agent $i$, so every agent $j \in [n] \setminus \{i\}$
has at most one good from $G$, so $|G| \le n-1$.
If $v_i(B_i) < v_i(n)$, then $G \supseteq [n]$, which is a contradiction.
Hence, $v_i(A_i) \ge v_i(B_i) \ge v_i(n)$.

Suppose $v_i(A_i) \ge v_i(n)$. Let $B$ be an allocation where we give
exactly one good from $[n-1]$ to each agent in $[n] \setminus \{i\}$,
and allocate $[m] \setminus [n-1]$ to agent $i$.
Then $B$ is EF1-fair to $i$ and $v_i(A_i) \ge v_i(n) = v_i(B_i)$.
Hence, $B$ is an M1S-certificate for agent $i$ for allocation $A$.
Hence, $A$ is M1S-fair to agent $i$.
\end{proof}

\begin{lemma}
\label{thm:ud:mms}
Consider a fair division instance $([n], [m], (v_i)_{i=1}^n, \eqEnt)$ over goods
where $v_i$ is unit-demand for some agent $i$.
\WLoG, let $v_i(1) \ge \ldots \ge v_i(m)$.
Then agent $i$'s maximin share is $v_i(n)$.
\end{lemma}
\begin{proof}
In every $n$-partition $P$ of $[m]$, some bundle $P_k$ does not contain a good from $[n-1]$.
Then $v_i(P_k) \le v_i(n)$. Hence, $\MMS_i \le v_i(n)$.
Let $P$ be a partition where $P_j = \{j\}$ for $j \in [n-1]$ and $P_n = [m] \setminus [n-1]$.
Then $\min_{j=1}^n v_i(P_j) = v_i(n)$. Hence, $\MMS_i = v_i(n)$.
\end{proof}

\begin{lemma}
\label{thm:ud:aps}
Consider a fair division instance $([n], [m], (v_i)_{i=1}^n, \eqEnt)$ over goods
where $v_i$ is unit-demand for some agent $i$.
\WLoG, let $v_i(1) \ge \ldots \ge v_i(m)$.
Then agent $i$'s anyprice share is $v_i(n)$.
\end{lemma}
\begin{proof}
Set the price of the first $n-1$ goods to be $1/(n-1)$ each
and set the price of all the remaining goods to 0.
This tells us that $\APS_i \le v_i([m] \setminus [n-1]) = v_i(n)$.

For any non-negative price vector, some item from $[n]$ is affordable,
and gives value at least $v_i(n)$. Hence, $\APS_i \ge v_i(n)$.
\end{proof}

\begin{lemma}
\label{thm:ud:prop1}
Consider a fair division instance $([n], [m], (v_i)_{i=1}^n, \eqEnt)$ over goods
where $v_i$ is unit-demand for some agent $i$.
\WLoG, let $v_i(1) \ge \ldots \ge v_i(m)$.
Then every allocation is PROP1-fair to agent $i$.
\end{lemma}
\begin{proof}
Let $1 \in A_j$. If $j = i$, then $v_i(A_i) = v_i([m]) > v_i([m])/n$.
If $j \neq i$, then $v_i(A_i \cup \{1\}) = v_i([m]) > v_i([m])/n$.
\end{proof}
