\section{Fairness Notions}
\label{sec:notions}

We now list all the fairness notions we consider in this paper.
Due to the large number of notions we consider, we describe them briefly.
Details like motivation and examples can be found in the papers we cite for each notion,
or in the survey papers cited in \cref{sec:intro:related-work}.

\subsection{Envy-Based Notions}

\begin{definition}[EF]
\label{defn:ef}
Let $\Ical \defeq \fdInst{[n]}{[m]}{(v_i)_{i=1}^n}{w}$ be a fair division instance.
In an allocation $A$, an agent $i \in [n]$ \emph{envies} another agent
$j \in [n] \setminus \{i\}$ if $v_i(A_i)/w_i < v_i(A_j)/w_j$.
Agent $i$ is \emph{envy-free} in $A$ (or $A$ is EF-fair to $i$) if
she does not envy any other agent in $A$.
\end{definition}

For unequal entitlements, most papers use the term WEF (weighted EF) instead of EF.
But we use the term EF in this paper to emphasize that unequal entitlements
is a property of the fair division setting, not the fairness notion.
%
It is easy to see that EF allocations may not exist, so several relaxations have been studied.
Two of the most popular relaxations of EF are
EF1 (envy-free up to one item) \citep{budish2011combinatorial,lipton2004approximately},
and EFX (envy-free up to any item) \citep{caragiannis2019unreasonable}.

\begin{definition}[EF1]
\label{defn:ef1}
Let $\Ical \defeq \fdInst{[n]}{[m]}{(v_i)_{i=1}^n}{w}$ be a fair division instance.
In $\Ical$, an allocation $A$ is EF1-fair to agent $i$ if for every other agent $j$,
either $i$ does not envy $j$,
or $v_i(A_i)/w_i \ge v_i(A_j \setminus \{g\})/w_j$ for some $g \in A_j$,
or $v_i(A_i \setminus \{c\})/w_i \ge v_i(A_j)/w_j$ for some $c \in A_i$.

Equivalently, $A$ is EF1-fair to $i$ if for every other agent $j$
and some $S \subseteq A_i \cup A_j$ such that $|S| \le 1$, we have
$v_i(A_i \setminus S)/w_i \ge v_i(A_j \setminus S)/w_j$.
\end{definition}

EFX was originally defined by \citet{caragiannis2019unreasonable} for additive valuations over goods:
an agent $i$ \emph{strongly envies} an agent $j$ if,
even after removing a good of non-zero value from $j$'s bundle, agent $i$ still envies $j$.
An allocation is EFX-fair to agent $i$ if she does not strongly envy anyone.
We extend this definition to non-additive valuations over mixed manna.

%\begin{restatable}[EFX]{definition}{rDefnEfx}
\begin{definition}[EFX]
\label{defn:efx}
Let $\Ical \defeq \fdInst{[n]}{[m]}{(v_i)_{i=1}^n}{w}$ be a fair division instance.
In $\Ical$, an allocation $A$ is EFX-fair to agent $i$ if for each $j \in [n] \setminus \{i\}$,
either $i$ does not envy $j$, or both of the following hold:
\begin{enumerate}
\item Removing any positively-valued subset from $j$'s bundle eliminates $i$'s envy towards $j$:
\ifColsTwo
\[ \frac{v_i(A_i)}{w_i} \ge \frac{\max\left(\left\{
    \begin{array}{l}
    v_i(A_j \setminus S): S \subseteq A_j
    \\\quad \textrm{ and } v_i(S \mid A_i) > 0
    \end{array}\right\}\right)}{w_j}. \]
\else
\[ \frac{v_i(A_i)}{w_i} \ge \frac{\max(\{v_i(A_j \setminus S): S \subseteq A_j
    \textrm{ and } v_i(S \mid A_i) > 0\})}{w_j}. \]
\fi
\item Removing any negatively-valued subset from $i$'s bundle eliminates $i$'s envy towards $j$:
\ifColsTwo
\[ \frac{\min\left(\left\{
    \begin{array}{r}
    v_i(A_i \setminus S): S \subseteq A_i \textrm{ and }
    \\ v_i(S \mid A_i \setminus S) < 0
    \end{array}\right\}\right)}{w_i} \ge \frac{v_i(A_j)}{w_j}. \]
\else
\[ \frac{\min\left(\left\{v_i(A_i \setminus S): S \subseteq A_i
    \textrm{ and } v_i(S \mid A_i \setminus S) < 0 \right\}\right)}{w_i} \ge \frac{v_i(A_j)}{w_j}. \]
\fi
\end{enumerate}
\end{definition}

\Cref{defn:efx} looks different from the original definition by \citet{caragiannis2019unreasonable},
and also differs from \EFXZero, an alternative definition of EFX studied by many papers
\citep{plaut2020almost,chaudhury2021little,chaudhury2024efx}.
However, we show in \extCref{sec:notions:efx} that \cref{defn:efx} is equivalent to the original definition of EFX
for submodular valuations over goods and submodular valuations over chores,
and equivalent to \EFXZero{} when marginals are (strictly) positive or negative.
Thus, \cref{defn:efx} is a generalization of known definitions.
In \extCref{sec:notions:efx}, we give more details on our motivation for defining EFX this way.

\subsection{Proportionality-Based Notions}

\begin{definition}[PROP]
\label{defn:prop}
Let $\Ical \defeq \fdInst{[n]}{[m]}{(v_i)_{i=1}^n}{w}$ be a fair division instance.
For $\Ical$, agent $i$'s \emph{proportional share} is $w_i \cdot v_i([m])$.
Allocation $A$ is \emph{proportional} (PROP) if $v_i(A_i) \ge w_i \cdot v_i([m])$.
\end{definition}

A popular relaxation of PROP is PROP1 (proportional up to one item),
where each agent believes her bundle is better than the proportional share
after taking some good or giving away some chore.
% See \cref{defn:prop1} for a formal definition.

\begin{definition}[PROP1, \shortcite{conitzer2017fair}]
\label{defn:prop1}
Let $\Ical \defeq \fdInst{[n]}{[m]}{(v_i)_{i=1}^n}{w}$ be a fair division instance.
In $\Ical$, an allocation $A$ is PROP1-fair to agent $i$ if
either $v_i(A_i) \ge w_i \cdot v_i([m])$,
or $v_i(A_i \cup \{g\}) > w_i \cdot v_i([m])$ for some $g \in [m] \setminus A_i$,
or $v_i(A_i \setminus \{c\}) > w_i \cdot v_i([m])$ for some $c \in A_i$.
\end{definition}

Note that \cref{defn:prop1} uses strict inequalities, whereas most papers do not.
This definition is from \citet{feige2025low}, and we use it to make PROP1
a slightly stronger notion without altering its fundamental properties.
See \extCref{sec:notions:prop1} for details.

PROPx (PROP up to any item) \citep{aziz2020polynomial,li2022almost} is another relaxation of PROP.
It was originally defined for additive valuations over goods \citep{aziz2020polynomial}:
an agent $i$ is PROPx-satisfied if transferring any good to her bundle makes her proportionally-satisfied.
We extend this definition to non-additive valuations over mixed manna.

\begin{definition}[PROPx]
\label[definition]{defn:propx}
For a fair division instance $\Ical \defeq \fdInst{[n]}{[m]}{(v_i)_{i=1}^n}{w}$,
an allocation $A$ is said to be PROPx-fair to agent $i$ iff
either $v_i(A_i) \ge w_i \cdot v_i([m])$ or both of these conditions hold:
\begin{tightenum}
\item $v_i(A_i \cup S) > w_i \cdot v_i([m])$ for every $S \subseteq [m] \setminus A_i$
    such that $v_i(S \mid A_i) > 0$.
\item $v_i(A_i \setminus S) > w_i \cdot v_i([m])$ for every $S \subseteq A_i$
    such that $v_i(S \mid A_i \setminus S) < 0$.
\end{tightenum}
\end{definition}

\Cref{defn:propx} differs from \citet{aziz2020polynomial} and \citet{li2022almost} in two ways.
First, we use strict inequalities in \cref{defn:propx}, similar to our definition of PROP1.
Second, we replaced `transferring a good' by `transferring a positive-valued subset',
and `transferring out a chore' by `transferring out a negative-valued subset',
similar to our definition of EFX. We prove in \extCref{sec:notions:propx} that,
just like with EFX, our definition of PROPx simplifies for submodular valuations over goods,
for submodular valuations over chores, and for (strictly) positive or negative marginals.

PROPavg (PROP up to the min-avg item) \citep{kobayashi2025proportional},
and PROPm (PROP up to the minimax item) \citep{baklanov2021achieving}
are strengthenings of PROP1 and relaxations of PROPx.
We formally describe them in Appendices \extRef{sec:notions:propx} and \extRef{sec:notions:propm-propavg}.
Just like PROPx, our formal definitions for PROPm and PROPavg differ from the original definitions,
and our definitions simplify for special cases. See \extCref{sec:notions:propx,sec:notions:propm-propavg} for details.

\subsection{Maximin Share and AnyPrice Share}

For equal entitlements, an agent's maximin share (MMS) \citep{budish2011combinatorial}
is the maximum value she can obtain by partitioning the goods into $n$ bundles and picking the worst one.
An allocation is MMS-fair to her if her bundle's value is at least her maximin share.

\begin{definition}[MMS, \citet{budish2011combinatorial}]
\label[definition]{defn:mms-simple}
Let $\fdInst{[n]}{[m]}{(v_i)_{i=1}^n}{\eqEnt}$ be a fair division instance.
Let $\Pi_n([m])$ be the set of all $n$-partitions of $[m]$.
Define agent $i$'s \emph{maximin share} to be
\[ \MMS_i \defeq \max_{P \in \Pi_n(M)} \min_{j=1}^n v_i(P_j). \]
An allocation $A$ is \emph{MMS-fair} to agent $i$ if $v_i(A_i) \ge \MMS_i$.
\end{definition}

Weighted MMS (WMMS) \citep{farhadi2019fair} and pessimistic share (pessShare) \citep{babaioff2023fair}
are well-known extensions of MMS to the unequal entitlements setting.
See \extCref{sec:notions:mms} for details.

AnyPrice Share (APS) \citep{babaioff2023fair} is another fairness notion that is inspired by MMS.

\begin{definition}[APS, \citet{babaioff2023fair}]
\label[definition]{defn:aps-simple}
For a fair division instance $\Ical \defeq \fdInst{[n]}{[m]}{(v_i)_{i=1}^n}{w}$,
agent $i$'s AnyPrice Share (APS) is defined as
\[ \APS_i \defeq \min_{p \in \mathbb{R}^m}\;\max_{S \subseteq [m]: p(S) \le w_i \cdot p([m])} v_i(S). \]
Here $p$ is called the \emph{price vector}.
An allocation $A$ is APS-fair to agent $i$ if $v_i(A_i) \ge \APS_i$.
\end{definition}

See \extCref{sec:notions:aps} for an alternative equivalent definition of APS, called the \emph{dual definition}.

\subsection{Derived Notions}

New fairness notions can be obtained by systematically modifying existing notions.
%
We start with two related concepts, epistemic fairness \citep{aziz2018knowledge,caragiannis2023new}
and minimum fair share \citep{caragiannis2023new}.

\begin{definition}[epistemic fairness]
\label{defn:epistemic}
Let $F$ be a fairness notion.
An allocation $A$ is \emph{epistemic-$F$-fair} to an agent $i$ if
there exists another allocation $B$ that is $F$-fair to agent $i$ and $B_i = A_i$.
$B$ is called agent $i$'s \emph{epistemic-$F$-certificate} for $A$.
\end{definition}

\begin{definition}[minimum fair share]
\label{defn:minfs}
For a fair division instance $\Ical \defeq \fdInst{[n]}{[m]}{(v_i)_{i=1}^n}{w}$
and fairness notion $F$, let $\Acal(\Ical, F, i)$ be the set of allocations
that are $F$-fair to agent $i$.
%
Then $A$ is minimum-$F$-share-fair to agent $i$ if there exists
an allocation $B \in \Acal(\Ical, F, i)$ such that $v_i(A_i) \ge v_i(B_i)$.
Then $B$ is called agent $i$'s \emph{minimum-$F$-share-certificate} for $A$.
%
Equivalently, an allocation $A$ is \emph{minimum-$F$-share-fair} to agent $i$ if
$v_i(A_i)$ is at least her minimum-$F$-share, defined as
\[ \minFS(\Ical, F, i) \defeq \min_{X \in \Acal(\Ical, F, i)} v_i(X_i). \]
\end{definition}

We now describe pairwise \citep{caragiannis2019unreasonable}
and groupwise \citep{barman2018groupwise} fairness.

\begin{definition}[restricting, pairwise and groupwise fairness]
\label{defn:restricting}
\label{defn:pairwise}
\label{defn:groupwise}
Let $\Ical \defeq \fdInst{N}{M}{(v_i)_{i \in N}}{w}$ be a fair division instance and $A$ be an allocation.
For a subset $S \subseteq N$ of agents, where $|S| \ge 2$,
let $\restrict(\Ical, A, S)$ be the pair $(\Ical^{(S)}, A^{(S)})$, where
allocation $A^{(S)} \defeq (A_j)_{j \in S}$,
instance $\Ical^{(S)} \defeq \fdInst{S}{\bigcup_{j \in S} A_j}{(v_j)_{j \in S}}{\what}$,
and weights $\what_j \defeq w_j / \sum_{k \in S} w_k$.

$A$ is \emph{pairwise-$F$-fair} to agent $i$ if for all $j \in N \setminus \{i\}$,
$A^{(\{i, j\})}$ is $F$-fair to $i$ in the instance $\Ical^{(\{i, j\})}$.
$A$ is \emph{groupwise-$F$-fair} to agent $i$ if for all $S \subseteq N \setminus \{i\}$,
$A^{(\{i\} \cup S)}$ is $F$-fair to $i$ in the instance $\Ical^{(\{i\} \cup S)}$.
\end{definition}

In this paper, we consider these derived notions:
%\begin{tightenum}
Epistemic envy-freeness (EEF), epistemic EFX (EEFX), epistemic EF1 (EEF1),
minimum EF share (MEFS), minimum EFX share (MXS), minimum EF1 share (M1S),
pairwise proportionality (PPROP), pairwise MMS (PMMS), pairwise APS (PAPS),
groupwise proportionality (GPROP), groupwise MMS (GMMS), groupwise APS (GAPS).
%\end{tightenum}
